---
title: "Study1_ProcessData"
author: "Shari Liu"
date: '2022-09-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
pacman::p_load(tidyverse,
               conflicted,
               here,
               janitor,
               cowplot,
               data.table,
               corrplot,
               viridis,
               psych,
               factorextra,
               cluster)

conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("rename", "dplyr")
conflict_prefer("summarise", "dplyr")
conflict_prefer("lmer", "lmerTest")
conflict_prefer("here", "here")
conflict_prefer("arrange", "dplyr")
source(here("helper_funs.R"))

sessionInfo()
theme_set(theme_cowplot(10))

```

# Overview
This script processes Study 1 data for univariate and multivariate analysis. All instances of `saveRDS` have been commented out to avoid writing over existing files. Uncomment those statements in order to reproduce these steps and save (new) outputs.

# (1) Set up univariate data

```{r}
# read in data, and information about ROIs
factors <-
  c("ROI_name", "event", "top_n_voxels", "domain", "event", "task", "extracted_copes_main_condition", "extracted_run_number")

study1.data0 <-
  read.csv(
    here("input_data/Exp1_ROI_analysis_outputs_finalparcels_VOEsplitreps_Apr05_2023_convertVectors.csv"
    )
  ) %>%
  separate(
    col = "extracted_copes_main_condition",
    into = c("domain", "task", "event", "rep") ,
    sep = "_",
    remove = FALSE
  ) %>%
  rename(meanbeta = mean_topVoxels_main_condition_copes,
         top_n_voxels = top_voxel_selection_method) %>%
  mutate_at(factors, as.factor) %>%
  unique() %>%
  mutate(vis_statistics_video_group = case_when(task == "efficiency" ~ "psychology_efficiency_exp1",
                                                task == "goal" ~ "psychology_goal_exp1",
                                                task == "solidity" ~ "physics_solidity-exp1_block",
                                                task == "support" ~ "physics_support-exp1_ball"))

region_info <- read.csv(here("input_data/manyregions_info.csv")) %>%
  filter(!str_detect(ROI_name_final, "MT"))

# Exp 1 does not include MT (no way to functionally ID)
study1.data <- full_join(study1.data0, region_info) %>%
  filter(!str_detect(ROI_name_final, "MT"))

study1.data$event <- relevel(study1.data$event, ref = "fam")
study1.data$rep <- as.ordered(study1.data$rep)
levels(study1.data$task) <- c("efficiency", "goal", "solidity", "support")
```

```{r}
# checking that all regions are represented across the two data sources
regions1 <- unique(region_info$ROI_name) %>% sort()
regions2 <- unique(study1.data$ROI_name) %>% sort()
regions1 == regions2
```

```{r}
# are the number of observations per region per subject expected? n_observations should be 24 per run, 96 for 4 runs
study1.data %>%
  group_by(top_n_voxels, subjectID, ROI_name) %>%
  summarise(n_observations = n())

# check for duplicates
study1.data %>%
  # filter(subjectID == "sub-SAXNES2s028") %>%
  get_dupes(vector1_topVoxels_main_condition_copes) %>%
  group_by(top_n_voxels, subjectID, ROI_name, extracted_run_number) %>%
  summarise(n_duplicates = n()) 

```

```{r}
str(study1.data)
```

## Join with visual statistic info
```{r}
# read in visual stats data
vis_stats_info_exp1 <- read.csv(here("../../exp2/analysis_scripts/outputs/visual_statistics/visual_statistics_exp1_new.csv")) %>% select(-X, -domain, -task) %>%
  filter(in_exp1 == TRUE) %>%
  select(-value) %>%
  pivot_wider(names_from = metric, values_from = normalized_value, id_cols = c(vis_statistics_video_group, event))

study1.data.full <- left_join(study1.data, vis_stats_info_exp1, by = c("vis_statistics_video_group", "event")) %>%
  # select(-X) %>%
  filter(!is.na(top_n_voxels))  %>%
  unite("video", c("domain", "task", "event"), remove = FALSE)

# write_rds(study1.data.full, here("outputs/univariate_data/study1_univariate_data_singlebetas.Rds"))

```


## Summary statistics

```{r cars}
summary_task <-
  summarySEwithin(
    data = study1.data,
    measurevar = "meanbeta",
    withinvars = c("top_n_voxels", "ROI_name_final", "ROI_category", "focal_region", "old_ROI", "extracted_run_number", "domain", "task", "event"),
    idvar = "subjectID"
  )

summary_domain <-
  summarySEwithin(
    data = study1.data,
    measurevar = "meanbeta",
    withinvars = c("top_n_voxels", "ROI_name_final", "ROI_category", "focal_region", "old_ROI", "extracted_run_number", "domain", "event"),
    idvar = "subjectID"
  )
```

```{r}
# saveRDS(summary_domain, here("outputs", "univariate_descriptive_summaries", "study1_univariate_summary_domain_allvoxelN.Rds"))

# saveRDS(summary_task, here("outputs", "univariate_descriptive_summaries", "study1_univariate_summary_task_allvoxelN.Rds"))
```



# (2) Set up multivariate data

```{r}
study1.data <- read_rds(here("outputs", "univariate_data", "study1_univariate_data_singlebetas.Rds")) %>% 
  filter(extracted_run_number == "run1",
         top_n_voxels == 100) # run1 only

# first we need to unpack vectors into their own columns 
MVPA_vectors0 <- study1.data %>%
  select(top_n_voxels,
         focal_region,
         subjectID,
         ROI_name_final,
         ROI_category,
         extracted_run_number,
         contrast_for_topVoxel_selection,
         extracted_copes_main_condition,
         domain,
         task,
         event,
         rep,  ## only relevant for analysis that splits conditions by repetition (2 per run)
         vector1_topVoxels_main_condition_copes)


MVPA_vectors <- data.frame()
top_vox <- 100

for (n in top_vox) {
  cur_subset <- MVPA_vectors0 %>%
    filter(top_n_voxels == n)

  for (i in 1:nrow(cur_subset)) {
    # get all relevant info associated with each cope vector
    top_n_voxels <- cur_subset$top_n_voxels[i]
    focal_region <- cur_subset$focal_region[i]
    subj <- cur_subset$subjectID[i]
    ROI <- cur_subset$ROI_name_final[i]
    ROI_category <- cur_subset$ROI_category[i]
    selection_contrast <-
      cur_subset$contrast_for_topVoxel_selection[i]
    extracted_run_number <- cur_subset$extracted_run_number[i]
    domain <- cur_subset$domain[i]
    task <- cur_subset$task[i]
    event <- cur_subset$event[i]
    rep <- cur_subset$rep[i]  ## only relevant for analysis that splits conditions by repetition (2 per run)
    cond <- cur_subset$extracted_copes_main_condition[i]

    # get the cope vector and convert into cols (Vox1-100)
    copes <- cur_subset$vector1_topVoxels_main_condition_copes[i] %>%
      as.vector() %>%
      str_split(., pattern = " ") %>%
      flatten_chr() %>%
      str_remove_all(., pattern = ",") %>%
      str_remove_all(., pattern = "\n") %>%
      str_remove_all(., pattern = "]") %>%
      str_remove_all(., pattern = "\\[") %>%
      as.numeric() %>%
      na.omit() %>%
      t() %>%
      as.data.frame()

    length_cope_actual <- length(copes)

    cur.row <- cbind(
      top_n_voxels,
      length_cope_actual,
      focal_region,
      subj,
      ROI,
      selection_contrast,
      extracted_run_number,
      domain,
      task,
      event,
      rep,
      cond,
      copes
    )
    newlist <- list(MVPA_vectors, cur.row)
    MVPA_vectors <- rbindlist(newlist, fill = TRUE)
    # MVPA_vectors <- plyr::rbind.fill(MVPA_vectors, cur.row)
  }
}



# saveRDS(MVPA_vectors, here("outputs", "multivariate_data", "study1_multivariate_data_run1_allregions_top100.Rds"))
```

## Set up distances

```{r}
MVPA_vectors <- readRDS(here("outputs", "multivariate_data", "study1_multivariate_data_run1_allregions_top100.Rds"))

str(MVPA_vectors)
# are the number of observations per region per subject expected? n_observations should be 24
sum(MVPA_vectors$length_cope_actual != MVPA_vectors$top_n_voxels)
```

```{r, include = FALSE}

subjects <- levels(as.factor(MVPA_vectors$subj))
ROIs <- levels(as.factor(MVPA_vectors$ROI))

# z score vectors within voxels within ROIs within subjects
MVPA_vectors_zscored0 <- MVPA_vectors %>%
  filter(top_n_voxels == "100") %>%
  select(1:112) %>%
  gather(voxel, beta, V1:V100) %>%
  group_by(subj, ROI, voxel) %>%
  mutate(zscore_perROI_persubj = (beta - mean(beta)) / sd(beta)) %>%   
  ungroup() %>% 
  as.data.frame()

MVPA_vectors_zscored <- MVPA_vectors_zscored0 %>%
  select(-beta) %>% 
  spread(voxel, zscore_perROI_persubj)

# saveRDS(MVPA_vectors_zscored, here("outputs", "multivariate_data", "study1_multivariate_data_zscored_allregions_top100.Rds"))
```

```{r, include = FALSE}

MVPA_data <-
  readRDS(here("outputs",
               "multivariate_data",
               "study1_multivariate_data_run1_allregions_top100.Rds")) %>%
  filter(extracted_run_number == "run1")

MVPA_data_zscored <-
  readRDS(here("outputs", 
               "multivariate_data",
               "study1_multivariate_data_zscored_run1_allregions_top100.Rds")
  )


distance_metrics <- c("Euclidean", "Pearson")
labels <- c('euclidean', 'pearson')

ROIs <- unique(sort(MVPA_data$ROI))
subjects <- unique(sort(MVPA_data$subj))

top_nox <- 100
for (distance_metricI in 1:length(distance_metrics)) {
  distance_metric <- distance_metrics[distance_metricI]
  distance_metric_lower <- tolower(distance_metric)
  distance_metric_label <- labels[distance_metricI]
  
  # initialize final CSV output
  similarity_output_matrix <- data.frame()
  
  # GET EMPIRICAL RDMS
  # for each subject and ROI...
  for (i in 1:length(subjects)) {
    for (k in 1:length(ROIs)) {
      for (n in top_vox) {
        # get data specific to subject and ROI
        
        last_vox_column <- paste0("V", n)
        subjROIdata <- MVPA_data_zscored %>%
          filter(subj == subjects[i],
                 event != "fam", # only take test events
                 ROI == ROIs[k],
                 top_n_voxels == n) %>%
          select(domain, task, event, cond, V1:all_of(last_vox_column)) %>%
          select(-domain,-task,-event) %>%
          as.data.frame()
        
        row.names(subjROIdata) <- subjROIdata$cond
        
        subjROIdata.final <- subjROIdata %>% select(-cond)
        
        # pearson
        if (distance_metric == 'Pearson') {
          distmatrix <-
            1 - cor(t(subjROIdata.final)) # convert similarity into a distance (1-r)
        }
        
        # euclidian
        if (distance_metric == 'Euclidean') {
          distmatrix <-
            dist(
              subjROIdata.final,
              method = "euclidean",
              diag = TRUE,
              upper = TRUE
            ) %>% as.matrix()
        }
        
        cur.subset <- distmatrix %>%
          as.data.frame() %>%
          # select(-subj, -ROI, -dist) %>%
          flattenCorrMatrix(.) %>%
          unite(pair,
                c(row, column),
                sep = "-vs-",
                remove = FALSE) %>%
          rename(dist = cor) %>%
          mutate(subj = subjects[i],
                 ROI = ROIs[k],
                 distance_metric = distance_metric_label,
                 top_n_voxels = n)
        similarity_output_matrix <-
          rbind(similarity_output_matrix, cur.subset)
      }
    }
  }
  # save out RDM.empirical.model.distZ.all_iters
  fname =  paste0(
    here("outputs", "multivariate_data"),
    "MVPA_subject_RDMs_top100_",
    distance_metric,
    "_z.Rds",
    sep = ""
  )
  
  # saveRDS(similarity_output_matrix, fname)
}

```

```{r}
MVPA_subject_RDMs_Euclidean_zscored <- readRDS(here("outputs/multivariate_data/study1_MVPA_subject_RDMs_top100_Euclidean_z.Rds")) %>%
  mutate(distance_metric = "euclidean_zscored")

MVPA_subject_RDMs_Euclidean <- readRDS(here("outputs/multivariate_data/study1_MVPA_subject_RDMs_top100_Euclidean.Rds")) %>%
  mutate(distance_metric = "euclidean")

MVPA_subject_RDMs_Pearson_zscored <- readRDS(here("outputs/multivariate_data/study1_MVPA_subject_RDMs_top100_Pearson_z.Rds")) %>%
  mutate(distance_metric = "pearson_zscored")

MVPA_subject_RDMs_Pearson <- readRDS(here("outputs/multivariate_data/study1_MVPA_subject_RDMs_top100_Pearson.Rds")) %>%
  mutate(distance_metric = "pearson")

MVPA_combined_RDMs <- rbind(MVPA_subject_RDMs_Euclidean_zscored,
                            MVPA_subject_RDMs_Euclidean,
                            MVPA_subject_RDMs_Pearson_zscored,
                            MVPA_subject_RDMs_Pearson) %>%
  separate(row,
           c("row_domain", "row_task", "row_event", "row_rep"),
           remove = FALSE) %>%
  separate(column,
           c("column_domain", "column_task", "column_event", "column_rep"),
           remove = FALSE) %>%
  # for this col, we want to label all events matching on domain as within, not matching as between, and to drop adjacent test events
  mutate(pair_label_domain =
           case_when(
             ((row_task == column_task) &
                (row_rep == column_rep) & (row_event != column_event)
             ) ~ "drop",
             (row_domain == column_domain) ~ "within",
             TRUE ~ "between"
           )) %>%
  
  # for this col, we want to label all events matching on event as within, not matching as between, and to drop adjacent test events
  mutate(pair_label_event =
           case_when(
             ((row_task == column_task) &
                (row_rep == column_rep) & (row_event != column_event)
             ) ~ "drop",
             (row_event == column_event) ~ "within",
             TRUE ~ "between"
           )) %>%
  
  # same as matching by event, except we drop labels from the opposite domain
  mutate(
    pair_label_event_within_domain =
      case_when(
        ((row_task == column_task) &
           (row_rep == column_rep) & (row_event != column_event)
        ) ~ "drop",
        
        # same domain and event
        (pair_label_domain == "within" &
           pair_label_event == "within") ~ "within",
        
        # same domain, different event
        (pair_label_domain == "within" &
           pair_label_event == "between") ~ "between",
        
        # drop opposite domain
        pair_label_domain == "between" ~ "drop_domain"
      )
  ) %>%
  
  # domains within events (rather than events within domains)
  mutate(
    pair_label_domain_within_event =
      case_when(
        ((row_task == column_task) &
           (row_rep == column_rep) & (row_event != column_event)
        ) ~ "drop",
        
        # same domain, same event
        (pair_label_domain == "within" &
           pair_label_event == "within") ~ "within",
        
        # opposite domain
        (pair_label_domain == "between" &
           pair_label_event == "within")  ~ "between",
        
        # drop opposite event
        (pair_label_event == "between") ~ "drop_event"
      )
  ) %>%
  
  # events ACROSS domains (true "domain general" metric)
  mutate(
    pair_label_event_across_domains =
      case_when(
        ((row_task == column_task) &
           (row_rep == column_rep) & (row_event != column_event)
        ) ~ "drop",
        
        # same event, opposite domain
        (pair_label_domain == "between" &
           pair_label_event == "within") ~ "within",
        
        # different event, different domain
        (pair_label_domain == "between" &
           pair_label_event == "between")  ~ "between",
        
        # drop opposite event
        TRUE ~ "drop_event"
      )
  ) %>%
  
  # domains ACROSS events (true "event general" metric)
  mutate(
    pair_label_domains_across_events =
      case_when(
        ((row_task == column_task) &
           (row_rep == column_rep) & (row_event != column_event)
        ) ~ "drop",
        
        # same domain, opposite event
        (pair_label_event == "between" &
           pair_label_domain == "within") ~ "within",
        
        # different domain, different event
        (pair_label_event == "between" &
           pair_label_domain == "between")  ~ "between",
        
        # drop opposite event
        TRUE ~ "drop_event"
      )
  ) %>%
  
  mutate(same_domain = case_when(
    (
      # pair_label_dspecific_task != "drop_domain" |
        pair_label_event_within_domain != "drop_domain"
     & pair_label_domain == "within") ~ row_domain
  )) %>%
  
  mutate(
    same_event = case_when(
      pair_label_domain_within_event != "drop_event" &
        pair_label_event == "within" ~ row_event
    )
  ) %>%
  
  relocate(pair, .after = last_col())


```

```{r, include = TRUE}
ROIs <- levels(as.factor(MVPA_combined_RDMs$ROI))
subjects <- levels(as.factor(MVPA_combined_RDMs$subj))

RDMs <-
  c(
    "pair_label_event_within_domain",
    "pair_label_domain_within_event",
    "pair_label_event_across_domains",
    "pair_label_domains_across_events"
  )

MVPA_combined_RDMs_out0 <- MVPA_combined_RDMs %>%
  rename(ROI_name_final = ROI) %>%
  mutate_at(RDMs, as.factor) %>%
  mutate_at(RDMs, relev)

MVPA_combined_RDMs_out <-
  full_join(MVPA_combined_RDMs_out0, region_info, by = c("ROI_name_final")) 

MVPA_combined_RDMs_out$ROI_category <-
  factor(
    MVPA_combined_RDMs_out$ROI_category,
    levels = c("physics", "psychology", "MD", "early_visual")
  )

MVPA_combined_RDMs_out$distance_metric <-
  factor(
    MVPA_combined_RDMs_out$distance_metric,
    levels = c("euclidean", "euclidean_zscored", "pearson", "pearson_zscored")
  )

# saveRDS(MVPA_combined_RDMs_out, here("outputs/multivariate_data/study1_MVPA_processed_distances_top100.Rds"))
```


## Noise ceiling

## Compute the noise ceiling per ROI

```{r}
study1_distances <- readRDS(here("outputs/multivariate_data/study1_MVPA_processed_distances_top100.Rds"))
str(study1_distances)

subjects <- unique(study1_distances$subj)
ROIs <- unique(study1_distances$ROI_name_final)
```

```{r}

study1_distances_final <- study1_distances %>%
      filter(distance_metric == "euclidean",
             str_detect(pair, "fam", negate = TRUE))

noise_ceiling_acrossrun <- data.frame()

euclidean_dist <- function(x, y) sqrt(sum((x - y)^2))


for (ROI in ROIs) {
  for (subject in subjects) {
    
    # current subject
    cur_subject <- study1_distances_final %>%
      filter(subj == subject,
             ROI_name_final == ROI) %>%
      select(pair, dist) %>%
      arrange(pair)

    # everyone including current subject
    everyone <- study1_distances_final %>%
      filter(ROI_name_final == ROI) %>%
      group_by(pair) %>%
      summarise(dist_avg_everyone = mean(dist)) %>%
      arrange(pair)
    
    # everyone except the current subject    
    everyone_else <- study1_distances_final %>%
      filter(subj != subject,
             ROI_name_final == ROI) %>%
      group_by(pair) %>%
      summarise(dist_avg_everyonebutX = mean(dist)) %>%
      arrange(pair)
    
    # compute lower bound noise ceiling, excluding cur subj
    euclidean_cur_iteration_lowerbound <-
      euclidean_dist(cur_subject$dist,
          everyone_else$dist_avg_everyonebutX)
    
    kendall_cur_iteration_lowerbound <-
      cor(cur_subject$dist,
          everyone_else$dist_avg_everyonebutX,
          method = "kendall")
    
    # compute upper bound noise ceiling, including cur subj
    euclidean_cur_iteration_upperbound <-
      euclidean_dist(cur_subject$dist,
          everyone$dist_avg_everyone)
    
    kendall_cur_iteration_upperbound <-
      cor(cur_subject$dist,
          everyone$dist_avg_everyone,
          method = "kendall")
    
    cur_row <-
      cbind(subject, 
            ROI, 
            euclidean_cur_iteration_lowerbound,
            euclidean_cur_iteration_upperbound,
            kendall_cur_iteration_lowerbound,
            kendall_cur_iteration_upperbound
      )
    
    noise_ceiling_acrossrun <- rbind(noise_ceiling_acrossrun, cur_row)
  }
}

        

noise_ceiling_average_acrossrun <- noise_ceiling_acrossrun %>%
  mutate_at(c("kendall_cur_iteration_lowerbound",
              "kendall_cur_iteration_upperbound",
              "euclidean_cur_iteration_lowerbound",
              "euclidean_cur_iteration_upperbound"), as.numeric) %>%
  group_by(ROI) %>%
  summarise(kendall_ceiling_lowerbound_avg = mean(kendall_cur_iteration_lowerbound),
            kendall_ceiling_upperbound_avg = mean(kendall_cur_iteration_upperbound),
            euclidean_ceiling_lowerbound_avg = mean(euclidean_cur_iteration_lowerbound),
            euclidean_ceiling_upperbound_avg = mean(euclidean_cur_iteration_upperbound))

noise_ceiling_average_acrossrun_long <- noise_ceiling_average_acrossrun %>%
  gather(metric, value, kendall_ceiling_lowerbound_avg:euclidean_ceiling_upperbound_avg) %>%
  mutate(cor_metric = case_when(str_detect(metric, "kendall") ~ "kendall",
                                str_detect(metric, "euclidean") ~ "euclidean"
         ),
         upper_lower = case_when(str_detect(metric, "lower") ~ "lower",
                                 str_detect(metric, "upper") ~ "upper"))
```

```{r}
noise_ceiling_average_acrossrun_long_lower_upper <- noise_ceiling_average_acrossrun_long %>%
  pivot_wider(id_cols = c("ROI", "cor_metric"), names_from = c("upper_lower")) %>%
  group_by(ROI, cor_metric) %>%
  mutate(average = mean(c(lower, upper))) %>%
  ungroup() %>%
    rename(noiseceiling_lower = lower,
         noiseceiling_upper = upper,
         noiseceiling_average = average,
         ROI_name_final = ROI)


noise_ceiling_average_acrossrun_long_lower_upper_final <- left_join(noise_ceiling_average_acrossrun_long_lower_upper, region_info)
```

```{r}
# write_rds(noise_ceiling_average_acrossrun_long_lower_upper_final, path = here("outputs/multivariate_analysis_outputs/MVPA_noiseceiling_perROI.Rds"))
```

