---
title: "Violations of physical and psychological expectations in the human adult brain - Experiment 1 Univariate Analysis"
author: "Shari Liu"
date: '2023-08-01'
output:
  html_document:
    code_folding: hide
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: yes
    theme: spacelab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
pacman::p_load(tidyverse,
               ggforce,
               conflicted,
               here,
               cowplot,
               lme4,
               lmerTest,
               effects,
               performance,
               EMAtools,
               sjPlot,
               effectsize,
               lsmeans,
               patchwork,
               rmarkdown,
               DT,
               ggrepel,
               nptest,
               boot,
               boot.pval)

conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("rename", "dplyr")
conflict_prefer("mutate", "dplyr")
conflict_prefer("summarise", "dplyr")
conflict_prefer("lmer", "lmerTest")
conflict_prefer("here", "here")

source(here("helper_funs.R"))
options(contrasts = c("contr.sum", "contr.poly")) 

theme_set(theme_cowplot(10))

sessionInfo()
```

# Overview
This script:

- Part 1: visualizes and analyzes the mean amplitude of response (`meanbeta`) in 8 focal regions (left and right SMG, left and right STS, left and right V1, bilateral APC and RFC). 
- Part 2: does the same across other, non-focal ROIs.
- Part 3: visualizes and analyzes the reliability of domains with events and events within domains across all ROIs. This is the analog to the pre-registered MVPA analysis that is reported in the SI.

It also contains the code needed to reproduce Figure 3 in the main text of the paper. All instances of `write_rds`, `write_csv`, etc have been commented out to avoid writing over existing files. Uncomment those statements in order to reproduce these steps and save (new) outputs.

## Read in data
```{r}
univariate_data <- readRDS(here("outputs/univariate_data/study1_univariate_data_singlebetas.Rds"))
univariate_data$event <- relevel(as.factor(univariate_data$event), ref = "unexp")

univariate_summary_domain <- readRDS(here("outputs",
                                          "univariate_descriptive_summaries",
                                          "study1_univariate_summary_domain_allvoxelN.Rds"))

univariate_summary_task <- readRDS(here(
                                "outputs",
                            "univariate_descriptive_summaries",
 "study1_univariate_summary_task_allvoxelN.Rds"))
```

# PART 1: Focal regions

```{r}
focal_data <- univariate_data %>%
  filter(focal_region == 1)

focal_summary_domain <- univariate_summary_domain %>%
  filter(focal_region == 1)

focal_summary_task <- univariate_summary_task %>%
  filter(focal_region == 1)

domain_specific_regions <- c("physics", "psychology")
domain_general_regions <- c("early_visual", "MD")
```

```{r}
focal_data_100 <- focal_data %>%
  filter(top_n_voxels == "100")

focal_summary_domain_100 <- focal_summary_domain %>%
  filter(top_n_voxels == "100")

focal_summary_task_100 <- focal_summary_task %>%
  filter(top_n_voxels == "100")
```


## Does the VOE effect diminish in size over runs?

```{r, fig.height=10}
model_habituation <- lmer(data = focal_data_100 %>%
                            filter(ROI_category != "early_visual",
                                   event != "fam",
                                   ROI_category != "MD"), # cannot model MD regions because of non-independence of ROI selection (based on runs 2-4)
                          formula = meanbeta ~  extracted_run_number * event + (1|subjectID))
check_model(model_habituation)
plot(allEffects(model_habituation))

summary(model_habituation)


model_habituation_results <- cbind(gen.m(model_habituation), gen.ci(model_habituation)[3:10,])

model_habituation_results_byrun <- lsmeans(model_habituation, pairwise ~ event | extracted_run_number, pbkrtest.limit = 4352)$contrasts %>% as.data.frame()
```

```{r}
DT::datatable(model_habituation_results, options = list(scrollX = TRUE))

DT::datatable(model_habituation_results_byrun, options = list(scrollX = TRUE))
```

```{r, eval = FALSE}
# write_rds(model_habituation_results, path = here("outputs/univariate_results/habituation_over_runs_modelsummary.Rds"))
# write_rds(model_habituation_results_byrun, path = here("outputs/univariate_results/habituation_over_runs_perrun.Rds"))
```

## Visualize by domain

```{r plots}

regions <- levels(as.factor(focal_data$ROI_name_final))

plot_by_domain_run1 <- function(region, ymin, ymax) {
  plotobject <- ggplot(data = focal_summary_domain_100 %>% filter(str_detect(ROI_name_final, region), extracted_run_number == "run1", event != "fam"),
           aes(x = event, y = meanbeta, fill = domain)) +
      geom_bar(stat = "identity", aes(alpha = event), colour = "black") +
      geom_errorbar(
        aes(ymin = meanbeta - se, ymax = meanbeta + se),
        position = position_dodge(width = .9),
        width = .2,
        colour = "black"
      ) +
      theme_cowplot(10) +
      facet_wrap( ~ ROI_name_final + domain, nrow = 1) +
      scale_fill_manual(values = c("#00AFBB", "#FC4E07")) +
      ylab("Amplitude") +
      xlab("Event") +
      theme(axis.text.x = element_text(
        angle = 90,
        vjust = 0.5,
        hjust = 1
    ),
    legend.position = "none") +
    coord_cartesian(ylim = c(ymin, ymax)) +
    ggtitle(paste0("ROI:", region))
  
  plotobject
}
```

This plot is a subset of Figure 3 in the paper.

```{r}
SMG <- plot_by_domain_run1("supramarginal_", -1, 4) 

STS <- plot_by_domain_run1("superiortemporal_", 0, 4)

early_vis <- plot_by_domain_run1("V1_", 0, 11)

MD_APC <- plot_by_domain_run1("antParietal_bilateral", -1, 1)

MD_RFC <- plot_by_domain_run1("precentral_inferiorfrontal_R", -1, 1)

(SMG + STS) / (early_vis + MD_APC + MD_RFC) + plot_layout(widths = c(1, 1, 2, 1))
```


### Plot run by run (except for MD regions)

```{r plots2, fig.height= 12}
regions <- levels(as.factor(focal_data$ROI_name_final))

plot_by_domain_all_runs <- function(region, ymin, ymax) {
  plotobject <- ggplot(data = focal_summary_domain_100 %>% filter(str_detect(ROI_name_final, region)),
           aes(x = event, y = meanbeta, fill = domain)) +
      geom_bar(stat = "identity", aes(alpha = event), colour = "black") +
      geom_errorbar(
        aes(ymin = meanbeta - se, ymax = meanbeta + se),
        position = position_dodge(width = .9),
        width = .2,
        colour = "black"
      ) +
      theme_cowplot(10) +
      facet_wrap( ~ ROI_name_final + top_n_voxels + domain + extracted_run_number, nrow = 1) +
      scale_fill_manual(values = c("#00AFBB", "#FC4E07")) +
      ylab("Average beta (amplitude)") +
      xlab("Event") +
      theme(axis.text.x = element_text(
        angle = 90,
        vjust = 0.5,
        hjust = 1
    ),
    legend.position = "none") +
    coord_cartesian(ylim = c(ymin, ymax)) +
    ggtitle(paste0("ROI:", region))
  
  plotobject
}
```

```{r, out.width="100%", fig.height = 5}
plot_by_domain_all_runs("superiortemporal_L", -1, 3) | plot_by_domain_all_runs("superiortemporal_R", -1, 3)

plot_by_domain_all_runs("supramarginal_L", -1, 1) | plot_by_domain_all_runs("supramarginal_R", -1, 1)

plot_by_domain_all_runs("V1_L", -1, 7) | plot_by_domain_all_runs("V1_R", -1, 7)

plot_by_domain_run1("antParietal_bilateral", -1, 1) | plot_by_domain_run1("precentral_inferiorfrontal_R", -1, 1)
```

## Visualize by task
```{r}
regions <- levels(as.factor(focal_summary_task_100$ROI_name_final))

plot_univar_bytask <- function(region, ymin, ymax) {
  plotobject <- ggplot(data = focal_summary_task_100 %>% 
                         filter(str_detect(ROI_name_final, region),
                                extracted_run_number == "run1"),
           aes(x = event, y = meanbeta, fill = task)) +
      geom_bar(stat = "identity", aes(alpha = event), colour = "black") +
      geom_errorbar(
        aes(ymin = meanbeta - se, ymax = meanbeta + se),
        position = position_dodge(width = .9),
        width = .2,
        colour = "black"
      ) +
      # geom_point(data = focal_data_100 %>% filter(str_detect(ROI_name_final, region),
      #                                              extracted_run_number == "run1"),
      #            alpha = .1) +
      # geom_line(data = focal_data_100 %>% filter(str_detect(ROI_name_final, region)),
                # aes(group =
                      # subjectID),
                # alpha = .1) +
      theme_cowplot(10) +
      facet_wrap( ~ ROI_name_final + factor(task, c("solidity", "support", "goal", "efficiency")), nrow = 1) +
      scale_fill_manual(values = c("#deaf1f", "#f34b00", "#00aa8b", "#4f8e00")) +
      ylab("Average beta (amplitude)") +
      xlab("Event") +
      theme(axis.text.x = element_text(
        angle = 90,
        vjust = 0.5,
        hjust = 1
    ),
    legend.position = "none") +
    coord_cartesian(ylim = c(ymin, ymax)) +
    ggtitle(paste0("ROI:", region))
  
  plotobject
}
```

```{r, out.width="100%"}
plot_univar_bytask("superiortemporal_L", -1, 3) | plot_univar_bytask("superiortemporal_R", -1, 3)

plot_univar_bytask("supramarginal_L", -1, 3) | plot_univar_bytask("supramarginal_R", -1, 3)

plot_univar_bytask("V1_L", -1, 7) | plot_univar_bytask("V1_R", -1, 7)

plot_univar_bytask("antParietal_bilateral", -1, 3) | plot_univar_bytask("precentral_inferiorfrontal_R", -1, 3)

```

## Results

### Model fitting per domain
```{r, eval = FALSE}

effect_sizes_intercept_row <- data.frame(d = NA)
BF_intercept_row <- data.frame(BF = NA, BF_interpretation = NA)

rownames(effect_sizes_intercept_row) <- "(Intercept)"
rownames(BF_intercept_row) <- "(Intercept)"
rownames_no_intercept <- c("event1", "domain1", "rep.L", "event:domain")

data_formodeling <- univariate_data %>%
  filter(event != "fam")

data_formodeling %>%
  group_by(top_n_voxels) %>%
  summarise(n = n())


ROIs <- levels(as.factor(data_formodeling$ROI_name_final))
top_n_voxels <- unique(data_formodeling$top_n_voxels)
runs <- c("run1", "run2", "run3", "run4", "all_runs")
modelsummaries_init <- data.frame()

for (ROI in ROIs) {
  curROI <- ROI
  for (topN in top_n_voxels) {
    cur_top_voxels_N <- topN
    
    for (run in runs) {
      curRun <- run
      
      if (curRun != "all_runs") {
        ROIdata <- data_formodeling %>%
          filter(ROI_name_final == curROI,
                 top_n_voxels == topN,
                 extracted_run_number == curRun)
        model <- lmer(data = ROIdata,
                      formula = meanbeta ~ event * domain + rep + (1 |
                                                                     subjectID))
        
      } else if (curRun == "all_runs") {
        ROIdata <- data_formodeling %>%
          filter(ROI_name_final == curROI,
                 top_n_voxels == topN)
        model <- lmer(data = ROIdata,
                      formula = meanbeta ~ event * domain + rep + (1 |
                                                                     subjectID))
        
      }
      
      model_just_maineffects <-
        update(model, formula = ~ . - event:domain)  # Without interaction term
      model_just_domain <-
        update(model_just_maineffects, formula = ~ . - event)
      model_just_event <-
        update(model_just_maineffects, formula = ~ . - domain)
      
      model_no_rep <- update(model, formula = ~ . - rep)
      
      
      BF_BIC_interaction <-
        data.frame(BF = exp((
          BIC(model_just_maineffects) - BIC(model)
        ) / 2),
        BF_interpretation = interpret_bf(exp((
          BIC(model_just_maineffects) - BIC(model)
        ) / 2)))  # BICs to Bayes factor
      
      BF_BIC_event <-
        data.frame(BF = exp((
          BIC(model_just_domain) - BIC(model_just_maineffects)
        ) / 2),
        BF_interpretation = interpret_bf(exp((
          BIC(model_just_domain) - BIC(model_just_maineffects)
        ) / 2)))
      
      BF_BIC_domain <-
        data.frame(BF = exp((
          BIC(model_just_event) - BIC(model_just_maineffects)
        ) / 2),
        BF_interpretation = interpret_bf(exp((
          BIC(model_just_event) - BIC(model_just_maineffects)
        ) / 2)))
      
      BF_BIC_rep <-
        data.frame(BF = exp((BIC(model_no_rep) - BIC(model)) / 2),
                   BF_interpretation = interpret_bf(exp((
                     BIC(model_no_rep) - BIC(model)
                   ) / 2)))
      
      BF_initial <- rbind(BF_BIC_event,
                          BF_BIC_domain,
                          BF_BIC_rep,
                          BF_BIC_interaction)
      
      rownames(BF_initial) <- rownames_no_intercept
      BFs <- rbind(BF_intercept_row,
                   BF_initial)
      
      effect_sizes_initial <- lme.dscore(model, ROIdata, "lme4") %>%
        select(d)
      effect_sizes <-
        rbind(effect_sizes_intercept_row, effect_sizes_initial)
      
      if (ROIdata$ROI_category[1] %in% domain_specific_regions) {
        ROI_category <- "domain_specific"
      } else {
        ROI_category <- "domain_general"
      }
      
      ROI_focal <- ROIdata$focal_region[1]
      modelsummary <-
        cbind(
          cur_top_voxels_N,
          curRun,
          ROI_category,
          ROI_focal,
          curROI,
          rownames(summary(model)$coefficients),
          summary(model)$coefficients,
          confint.merMod(model)[3:7, ],
          effect_sizes,
          BFs
        ) %>%
        as.data.frame()
      
      colnames(modelsummary) <-
        c(
          "top_n_voxels",
          "extracted_run_number",
          "domain",
          "focal_region",
          "ROI",
          "effect",
          "B",
          "SE",
          "df",
          "t",
          "p",
          "CI_95_lower",
          "CI_95_upper",
          "d",
          "BF",
          "BF_interpretation"
        )
      modelsummaries_init <-
        rbind(modelsummaries_init, modelsummary)
      
      cat(
        tab_model(
          model,
          show.std = TRUE,
          show.se = TRUE,
          show.stat = TRUE,
          auto.label = TRUE,
          title = paste0("Univariate ROI results in: ", curROI)
        )$knitr,
        "  \n  \n"
      )
    }
  }
}


```

```{r, eval = FALSE}
modelsummaries <- modelsummaries_init %>%
  mutate_at(c(7:15), as.numeric) %>%
  mutate(star = as.factor(
           case_when(p < .001 ~ "***",
                     p < .01 ~ "**",
                     p < .05 ~ "*",
                     p < .1 ~ "~",
                     TRUE ~ " ")
         )) %>%
  mutate(p = round(p, digits = 3))

modelsummaries$effect <-
  as.factor(modelsummaries$effect)

levels(modelsummaries$effect) <-
  c("intercept", "domain", "event", "event:domain", "rep")
rownames(modelsummaries) <- NULL
```

```{r}
# write_rds(modelsummaries, here("outputs", "univariate_results", "modelsummaries_allregions_alltopN.Rds"))
```

```{r}
focal_modelsummaries <- read_rds(here("outputs/univariate_results/modelsummaries_allregions_alltopN.Rds")) %>%
  filter(focal_region == 1) 

DT::datatable(focal_modelsummaries %>% filter(top_n_voxels == "100", focal_region == 1) %>% arrange(effect), options = list(scrollX = TRUE,
                                                                                                                            pageLength = 100))
  # filter(extracted_run_number == "all_runs" | extracted_run_number == "run1") %>%
```

#### LSMG

```{r}
LSMG_model <- lmer(data = univariate_data %>%
                     filter(top_n_voxels == "100",
                            event != "fam",
                            extracted_run_number == "run1", 
                            ROI_name_final == "supramarginal_L"),
                   formula = meanbeta ~ event * domain + rep + (1|subjectID))

LSMG_results_bydomain_top100 <- lsmeans(LSMG_model, pairwise ~ event | domain)$contrasts %>% as.data.frame()

DT::datatable(LSMG_results_bydomain_top100, options = list(scrollX = TRUE))
# write_rds(LSMG_results_bydomain_top100, path = here("outputs/univariate_results/LSMG_results_bydomain_top100.Rds"))
```

#### RSMG

```{r}
RSMG_model <- lmer(data = univariate_data %>%
                     filter(top_n_voxels == "100",
                            event != "fam",
                            extracted_run_number == "run1", 
                            ROI_name_final == "supramarginal_R"),
                   formula = meanbeta ~ event * domain + rep + (1|subjectID))
summary(RSMG_model)
lsmeans(RSMG_model, pairwise ~ event | domain)$contrasts
```

#### LSTS

```{r}
LSTS_model <- lmer(data = univariate_data %>%
                     filter(top_n_voxels == "100",
                            event != "fam",
                            extracted_run_number == "run1", 
                            ROI_name_final == "superiortemporal_L"),
                   formula = meanbeta ~ event * domain + rep + (1|subjectID))
summary(LSTS_model)
lsmeans(LSTS_model, pairwise ~ event | domain)$contrasts
```

#### RSTS

```{r}
RSTS_model <- lmer(data = univariate_data %>%
                     filter(top_n_voxels == "100",
                            event != "fam",
                            extracted_run_number == "run1", 
                            ROI_name_final == "superiortemporal_R"),
                   formula = meanbeta ~ event * domain + rep + (1|subjectID))
summary(RSTS_model)
lsmeans(RSTS_model, pairwise ~ event | domain)$contrasts
```



### Model fitting per task
```{r, eval = FALSE}

effect_sizes_intercept_row <- data.frame(d = NA)
BF_intercept_row <- data.frame(BF = NA, BF_interpretation = NA)

rownames(effect_sizes_intercept_row) <- "(Intercept)"
rownames(BF_intercept_row) <- "(Intercept)"
rownames_no_intercept <- c("event1", "rep.L")

data_formodeling <- univariate_data %>%
  filter(event != "fam",
         top_n_voxels == 100)

data_formodeling %>%
  group_by(top_n_voxels) %>%
  summarise(n = n())

ROIs <- levels(as.factor(data_formodeling$ROI_name_final))
top_n_voxels <- unique(data_formodeling$top_n_voxels)
runs <- c("run1", "all_runs")

tasks <- unique(data_formodeling$task)
ROIs <- unique(data_formodeling$ROI_name_final)
data_formodeling$event <- relevel(data_formodeling$event, ref = "unexp")

modelsummaries_pertask_init <- data.frame()



for (ROI in ROIs) {
  curROI <- ROI
  for (task in tasks) {
    cur_task <- task
    
    for (run in runs) {
      if (run == "run1") {
        ROIdata <-
          data_formodeling %>% filter(ROI_name_final == curROI,
                                      task == cur_task,
                                      extracted_run_number == "run1")
      } else if (run == "all_runs")
        ROIdata <-
          data_formodeling %>% filter(ROI_name_final == curROI,
                                      task == cur_task)
      
        model <- lmer(data = ROIdata,
                      formula = meanbeta ~ event + rep + (1 | subjectID)) # had to remove run random int (convergence))

      focal_region <- ROIdata$focal_region[1]
      task_domain <- as.character(ROIdata$domain[1])
      ROI_category <- ROIdata$ROI_category[1]

      
      model_null <-
        update(model, formula = ~ . - event)  # Without interaction term
      
      model_norep <-
        update(model, formula = ~ . - rep)  # Without interaction term
  
      BF_BIC_event <-
        data.frame(BF = exp((BIC(model_null) - BIC(model)) / 2),
                   BF_interpretation = interpret_bf(exp((
                     BIC(model_null) - BIC(model)
                   ) / 2)))  # BICs to Bayes factor
      
      BF_BIC_rep <-
        data.frame(BF = exp((BIC(model_norep) - BIC(model)) / 2),
                   BF_interpretation = interpret_bf(exp((
                     BIC(model_norep) - BIC(model)
                   ) / 2)))  # BICs to Bayes factor      
      # BF_initial <- rbind(BF_BIC_event)
      
      
      BFs <- rbind(BF_intercept_row,
                   BF_BIC_event,
                   BF_BIC_rep)
      
      rownames(BFs)[2:3] <- rownames_no_intercept
      
      effect_sizes_initial <- lme.dscore(model, ROIdata, "lme4") %>%
        select(d)
      effect_sizes <-
        rbind(effect_sizes_intercept_row, effect_sizes_initial)
      cur_top_voxels_N <- 100

      modelsummary <-
        cbind(
          cur_top_voxels_N,
          run,
          ROI_category,
          focal_region,
          curROI,
          cur_task,
          rownames(summary(model)$coefficients),
          summary(model)$coefficients,
          confint.merMod(model)[3:5, ],
          effect_sizes,
          BFs
        ) %>%
        as.data.frame()
      
      colnames(modelsummary) <-
        c(
          "top_n_voxels",
          "extracted_run_number",
          "domain",
          "focal_region",
          "ROI",
          "task",
          "effect",
          "B",
          "SE",
          "df",
          "t",
          "p",
          "CI_95_lower",
          "CI_95_upper",
          "d",
          "BF",
          "BF_interpretation"
        )
      
      
      modelsummaries_pertask_init <-
        rbind(modelsummaries_pertask_init, modelsummary)
      # model_parameters(model) %>% print_md()
      cat(
        tab_model(
          model,
          show.std = TRUE,
          show.se = TRUE,
          show.stat = TRUE,
          auto.label = TRUE,
          title = paste0(
            "Exploratory Univariate ROI results for the task ",
            cur_task,
            "in the region: ",
            curROI,
            "in ",
            curRun
          )
        )$knitr,
        "  \n  \n"
      )
    }
  }
}
```

```{r, eval = FALSE}
modelsummaries_pertask <- modelsummaries_pertask_init %>%
  mutate_at(c(8:16), as.numeric) %>%
  mutate(star = as.factor(
           case_when(p < .001 ~ "***",
                     p < .01 ~ "**",
                     p < .05 ~ "*",
                     p < .1 ~ "~",
                     TRUE ~ " ")
         )) %>%
  mutate(p = round(p, digits = 3))

modelsummaries_pertask$effect <-
  as.factor(modelsummaries_pertask$effect)

levels(modelsummaries_pertask$effect) <-
  c("intercept", "event", "rep")
rownames(modelsummaries_pertask) <- NULL
```

```{r}
# write_rds(modelsummaries_pertask, here("outputs", "univariate_results", "modelsummaries_allregions_pertask.Rds"))
```

```{r}
modelsummaries_pertask <- read_rds(here("outputs", "univariate_results", "modelsummaries_allregions_pertask.Rds"))

```

#### Plot model outputs
```{r}
focal_modelsummaries_pertask_forplotting <- modelsummaries_pertask %>%
  filter(top_n_voxels == "100",
         effect == "event",
         extracted_run_number == "run1",
         focal_region == 1)

focal_modelsummaries_pertask_forplotting$ROI <- factor(focal_modelsummaries_pertask_forplotting$ROI, levels = c("supramarginal_L", "supramarginal_R", "superiortemporal_L", "superiortemporal_R", "antParietal_bilateral", "precentral_inferiorfrontal_R", "V1_L", "V1_R"))


pertask_b <- ggplot(focal_modelsummaries_pertask_forplotting,
       aes(ROI, B, colour = task, group = task)) +
  geom_point() +
  geom_errorbar(
    aes(ymin = B - SE, ymax = B + SE, 
    colour = task),
    position = position_dodge(width = .9),
    width = .2
  ) +  
  # geom_line() +
  geom_hline(yintercept = 0) +
  facet_wrap( ~ task, nrow = 1) +
  scale_colour_manual(values = c("#deaf1f", "#f34b00", "#00aa8b", "#4f8e00")) +
  ylab("B and SE") +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 0.5,
    hjust = 1
  )) +
  coord_cartesian(ylim = c(-.5, .7))

perregion_b <- ggplot(focal_modelsummaries_pertask_forplotting,
       aes(task, B, colour = task, group = task)) +
  geom_point() +
  geom_errorbar(
    aes(ymin = B - SE, ymax = B + SE, 
    colour = task),
    position = position_dodge(width = .9),
    width = .2
  ) +  
  # geom_line() +
  geom_hline(yintercept = 0) +
  facet_wrap( ~ ROI, nrow = 1) +
  scale_colour_manual(values = c("#deaf1f", "#f34b00", "#00aa8b", "#4f8e00")) +
  ylab("B and SE") +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 0.5,
    hjust = 1
  )) +
  coord_cartesian(ylim = c(-.5, .7))
```


```{r}
pertask_b
perregion_b
```


## Sensitivity of focal region results to top voxel criteria 

```{r, out.width="100%"}

focal_modelsummaries$top_n_voxels <- factor(focal_modelsummaries$top_n_voxels, levels = c("10", "50", "100", "150", "200", "250", "300"))
focal_modelsummaries$extracted_run_number <- factor(focal_modelsummaries$extracted_run_number, levels = c("run1", "run2", "run3", "run4", "all_runs"))


ggplot(focal_modelsummaries %>%
         filter(extracted_run_number != "all_runs",
                ROI != "antParietal_bilateral",
                ROI != "precentral_inferiorfrontal_R",
                effect != "intercept",
                effect != "rep"),
       aes(extracted_run_number, d, colour = top_n_voxels)) +
  geom_point() +
  geom_line(aes(group = top_n_voxels)) +
  ylab("Cohen's D") +
  facet_wrap(~ effect + factor(ROI, levels = c("supramarginal_L", "supramarginal_R", "superiortemporal_L", "superiortemporal_R", "V1_L", "V1_R")), nrow = 3) +
  # coord_cartesian(ylim = c(-.75, 0.75)) +
  geom_hline(yintercept = 0) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
```



# PART 2: Other regions
```{r}

nonfocal_modelsummaries <- read_rds(here("outputs/univariate_results/modelsummaries_allregions_alltopN.Rds")) %>%
  filter(focal_region == 0) 

DT::datatable(nonfocal_modelsummaries %>% 
                filter(top_n_voxels == "100") %>% 
                arrange(effect), 
              options = list(scrollX = TRUE,
                             pageLength = 100))
```

# PART 3: Region by region univar effect size

Here we repeat the MVPA manyregions analysis, whose results are difficult to interpret given the lack of reliable multivariate signal towards unexpected events, despite clear univariate effects.

```{r}
data_for_modeling <- univariate_data %>%
  filter(event != "fam",
         top_n_voxels == "100") %>%
  filter(extracted_run_number == "run1") %>%
  filter(!str_detect(ROI_name_final, "bilateral"))

ROIs <- levels(as.factor(data_for_modeling$ROI_name_final))

effect_sizes_intercept_row <- data.frame(d = NA)

rownames(effect_sizes_intercept_row) <- "(Intercept)"
rownames_no_intercept <- c("event1")

```

```{r, eval = FALSE}
modelsummaries_init <- data.frame()

for (ROI in ROIs) {
  curROI <- ROI

  # FIRST COMPUTE EVENT EFFECT SIZES, FOR EACH DOMAIN
  physics_data <- data_for_modeling %>%
    filter(ROI_name_final == curROI,
           domain == "physics")
  
  psychology_data <- data_for_modeling %>%
    filter(ROI_name_final == curROI,
           domain == "psychology")
      
  # had to remove random intercept for runs (convergence))
  physics_model <- lmer(data = physics_data,
                formula = meanbeta ~ event + iqr_contrast + mean_luminance + mean_motion + mean_hsf + mean_lsf + mean_rect + mean_curv + (1|subjectID))
  
  psychology_model <- lmer(data = psychology_data,
                formula = meanbeta ~ event + (1|subjectID))
  
  physics_event_effect_size <- lme.dscore(physics_model, physics_data, "lme4") %>%
    select(d)
  psychology_event_effect_size <- lme.dscore(psychology_model, psychology_data, "lme4") %>%
    select(d)
  
  # SECOND COMPUTE DOMAIN EFFECT SIZES, FOR EACH EVENT
  expected_data <- data_for_modeling %>%
    filter(ROI_name_final == curROI,
           event == "exp")
  
  unexpected_data <- data_for_modeling %>%
    filter(ROI_name_final == curROI,
           event == "unexp")
  
  # had to remove random intercept for runs (convergence))
  exp_model <- lmer(data = expected_data,
                        formula = meanbeta ~ domain + (1 | subjectID))
  
  unexp_model <- lmer(data = unexpected_data,
                           formula = meanbeta ~ domain + (1 | subjectID))
  
  exp_domain_effect_size <-
    lme.dscore(exp_model, expected_data, "lme4") %>%
    select(d)
  unexp_domain_effect_size <-
    lme.dscore(unexp_model, unexpected_data, "lme4") %>%
    select(d)
  
  if (physics_data$ROI_category[1] == "MD" | physics_data$ROI_category[1] == "early_visual") {
    ROI_domain <- "general"
  } else {
    ROI_domain <- "specific"
  }
  
  modelsummary <-
    cbind(
      ROI_domain,
      physics_data$ROI_category[1],
      curROI,
      physics_event_effect_size,
      psychology_event_effect_size,
      exp_domain_effect_size,
      unexp_domain_effect_size
    ) %>%
    as.data.frame()
    
      modelsummaries_init <-
        rbind(modelsummaries_init, modelsummary)
}

```

```{r, eval = FALSE}
colnames(modelsummaries_init) <-
  c("ROI_domain",
    "ROI_category",
    "ROI",
    "physics_event_effect_size",
    "psychology_event_effect_size",
    "exp_domain_effect_size",
    "unexp_domain_effect_size"
  )
rownames(modelsummaries_init) <- NULL


# write_rds(modelsummaries_init, here("outputs/univariate_results/univar_manyregions_results.Rds"))
```


```{r}
univar_manyregions_results <- read_rds( here("outputs/univariate_results/univar_manyregions_results.Rds"))

```



```{r}
plot1 <- ggplot(univar_manyregions_results, aes(psychology_event_effect_size,       physics_event_effect_size)) +
    geom_hline(yintercept = 0, linetype = 'dotted') +
  geom_vline(xintercept = 0, linetype = 'dotted') +
  coord_cartesian(xlim = c(-0.5, 1), ylim = c(-0.5, 1)) +
  geom_point(aes(colour = ROI_category), size = 3) +
  geom_smooth(method = "lm") +
  facet_wrap(~ROI_domain, scales = "free") +
  # coord_cartesian(xlim = c(-1.5,1.5), ylim = c(-1.5,1.5)) +
  scale_colour_manual(values = c("#fb00d3", "#f8bf00", "#4894ff", "#f71d00")) +
  xlab("VOE Effect Size (d), Physics Events") +
  ylab("VOE Effect Size (d), Psychology Events") +
  ggtitle(label = "Exp 1 VOE effects for each domain across regions") +
  geom_text_repel(aes(label = ROI), size = 3) +
    theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        legend.position = "none")


plot2 <- ggplot(univar_manyregions_results, aes(exp_domain_effect_size, unexp_domain_effect_size)) +
  geom_hline(yintercept = 0, linetype = 'dotted') +
  geom_vline(xintercept = 0, linetype = 'dotted') +
  coord_cartesian(xlim = c(-1.2, 1.2), ylim = c(-1.2, 1.2)) +
  geom_point(aes(colour = ROI_category), size = 3) +
  geom_smooth(method = "lm") +
  facet_wrap(~ROI_domain, scales = "free") +
  # coord_cartesian(xlim = c(-1.5,1.5), ylim = c(-1.5,1.5)) +
  scale_colour_manual(values = c("#fb00d3", "#f8bf00", "#4894ff", "#f71d00")) +
  xlab("Domain Effect Size (d), Expected Events") +
  ylab("Domain Effect Size (d), Unexpected Events") +
  ggtitle(label = "Exp 1 Domain effects for each event across regions") +
  geom_text_repel(aes(label = ROI), size = 3) +
    theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        legend.position = "none")
```

```{r}
plot1
plot2
```

```{r}
# instead of testing whether the linear relationship between x and y is 0, 
# we test for independence instead. H0 is that x and y are independent; F_{XY}(x,y) = F_X(x) F_Y(y).
observed_cors_ind <- univar_manyregions_results %>%
  group_by(ROI_domain) %>%
  summarise(
    cor_domain_within_event =
      np.cor.test(
        exp_domain_effect_size,
        unexp_domain_effect_size,
        alternative = "two.sided",
        independent = TRUE
      )$estimate,
    
    p_domain_within_event =
      np.cor.test(
        exp_domain_effect_size,
        unexp_domain_effect_size,
        alternative = "two.sided",
        independent = TRUE
      )$p.value,
    
    cor_event_within_domain =
      np.cor.test(
        physics_event_effect_size,
        psychology_event_effect_size,
        alternative = "two.sided",
        independent = TRUE
      )$estimate,
    
    p_event_within_domain =
      np.cor.test(
        physics_event_effect_size,
        psychology_event_effect_size,
        alternative = "two.sided",
        independent = TRUE
      )$p.value
  )
```

```{r}
observed_cors_ind
```

```{r}
# write_rds(observed_cors_ind, path = here("outputs/univariate_results/study1_univar_manyregions_observed_cor.Rds"))
```

### Bootstrap stats
```{r}

set.seed(2020)
## First define a function to work out the difference of corrs:
diff_corr <- function(data, indices) {
  data <- data[indices,]
  cor1 <-
    np.cor.test(DS_results$exp_domain_effect_size,
                DS_results$unexp_domain_effect_size,
                alternative = "two.sided",
                independent = TRUE,
                parallel = TRUE)$estimate
  cor2 <-
    np.cor.test(
      data$psychology_event_effect_size,
      data$physics_event_effect_size,
      alternative = "two.sided",
      independent = TRUE,
      parallel = TRUE)$estimate

    return(cor1 - cor2)
}


```
```{r}
DS_results <- univar_manyregions_results %>%
  filter(ROI_domain == "specific")

DG_results <- univar_manyregions_results %>%
  filter(ROI_domain == "general")
```

### Domain specific

```{r}
doMC::registerDoMC(cores = 2)  # for running in parallel

# Then apply a bootstrap procedure with 4000 draws (uncomment to reproduce):
# res_boot_DS <- boot(
#   data = DS_results,
#   R = 4000,
#   statistic = diff_corr,
#   stype = "i"
# )

# saveRDS(res_boot_DS, here("outputs/univariate_results/study1_univariate_dsregions_4000perms_confirmatory.Rds"))

res_boot_DS <- read_rds(here("outputs/univariate_results/study1_univariate_dsregions_4000perms_confirmatory.Rds"))

## Retrieve the empirical 95% confidence interval:
ds_results <- append(boot.ci(res_boot_DS, type = "perc", conf = 0.95),boot.pval(res_boot_DS))

# saveRDS(ds_results, here("outputs/univariate_results/study1_univariate_dsregions_summary.Rds"))

```

### Domain general

```{r}
## Then apply a bootstrap procedure with 4000 draws (uncomment to reproduce):
# res_boot_DG <- boot(data = DG_results,
#                  R = 4000,
#                  statistic = diff_corr,
#                  stype = "i")

# saveRDS(res_boot_DG, here("outputs/univariate_results/study1_univariate_dgregions_4000perms_confirmatory.Rds"))
res_boot_DG <- readRDS(here("outputs/univariate_results/study1_univariate_dgregions_4000perms_confirmatory.Rds"))

plot(res_boot_DG)

## Retrieve the empirical 95% confidence interval:

dg_results <- append(boot.ci(res_boot_DG, type = "perc", conf = 0.95),boot.pval(res_boot_DG))
# saveRDS(dg_results, here("outputs/univariate_results/study1_univariate_dgregions_summary.Rds"))

```


