---
title: "4_Data_Codebooks"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: true
  pdf_document:
    toc: yes
    toc_depth: 4
    latex_engine: xelatex
---

Here we prepare codebooks for all input data from Exp 1.

```{r setup}
knitr::opts_chunk$set(
  warning = TRUE, # show warnings during codebook generation
  message = TRUE, # show messages during codebook generation
  error = TRUE, # do not interrupt codebook generation in case of errors,
                # usually better for debugging
  echo = TRUE  # show R code
)
ggplot2::theme_set(ggplot2::theme_bw())
library(pacman)
pacman::p_load(here,
               codebook,
               labelled,
               tidyverse)
```


# ROI data

Path: `input_data/Exp1_ROI_analysis_outputs_finalparcels_VOEsplitreps_Apr05_2023_convertVectors.csv`

Note - the size of this dataset is too big for the `codebook` package (548352 lines), so I filtered it down to just the data from the top 100 voxels. 

```{r prepare_codebook_1}
ROI_data <- rio::import(here("input_data/Exp1_ROI_analysis_outputs_finalparcels_VOEsplitreps_Apr05_2023_convertVectors.csv")) %>%
  filter(top_voxel_selection_method == "100")


var_label(ROI_data) <- list(
        top_voxel_selection_method = "Size of extracted ROI (# voxels)", 
        ROI_name = "",
        ROI_category = "Psychology, physics, early visual, or multiple demand ROI",
        n_voxels_in_brainmasked_parcel = "N voxels in parcel",
        subjectID = "",
        contrast_for_topVoxel_selection = "Contrast basis for ROI selection",
        selection_contrast_task_name = "Task basis for ROI selection",
        extracted_copes_main_condition = "Which condition copes were extracted from",
        extracted_run_number = "Which run (1-4) copes were extracted from",
        mean_topVoxels_main_condition_copes = "Mean response from ROI",
        vector1_topVoxels_main_condition_copes = "Vector of responses in ROI"
)

metadata_list(ROI_data)

metadata(ROI_data)$name <- "ROI data, Exp 1"
metadata(ROI_data)$description <- "ROI data from Exp1 in the manuscript entitled 'Violations of physical and psychological expectations in the human adult brain' by Liu et al."
metadata(ROI_data)$datePublished <- "2023-08-21"
metadata(ROI_data)$creator <- list(
      "@type" = "Person",
      givenName = "Shari", familyName = "Liu",
      email = "shariliu@jhu.edu", 
      affiliation = list("@type" = "Organization",
        name = "Johns Hopkins University, Baltimore, MD, USA"))
metadata(ROI_data)$citation <- "Liu, S., Lydic, K., Mei, L., & Saxe, R. (2023, preprint). Violations of physical and psychological expectations in the human adult brain."
metadata(ROI_data)$temporalCoverage <- "2023" 
```

```{r codebook_1}
codebook(ROI_data)
```

# Subject info

Path: `input_data/exp1_subject_info.csv`

```{r prepare_codebook_2}
subj_info <- rio::import(here("input_data/exp1_subject_info.csv"))


var_label(subj_info) <- list(
        experiment = "", 
        include = "Include subject in analysis?",
        exclude_why = "If exclude, why?",
        subjectID = "",
        gender = "Self-reported gender",
        handed = "Left or right handed",
        age = "Age in years at time of scan",
        data_sharing = "Consented to sharing de-faced images on OpenNeuro?"
)


metadata(subj_info)$name <- "Subject info, Experiment 1"
metadata(subj_info)$description <- "Subject information for the manuscript entitled 'Violations of physical and psychological expectations in the human adult brain' by Liu et al."
metadata(subj_info)$datePublished <- "2023-08-21"
metadata(subj_info)$creator <- list(
      "@type" = "Person",
      givenName = "Shari", familyName = "Liu",
      email = "shariliu@jhu.edu", 
      affiliation = list("@type" = "Organization",
        name = "Johns Hopkins University, Baltimore, MD, USA"))
metadata(ROI_data)$citation <- "Liu, S., Lydic, K., Mei, L., & Saxe, R. (2023, preprint). Violations of physical and psychological expectations in the human adult brain."
metadata(subj_info)$temporalCoverage <- "2023" 
```

```{r codebook_2}
codebook(subj_info)
```


# Region info

Path: `input_data/manyregions_info.csv`


```{r prepare_codebook_3}
region_info <- rio::import(here("input_data/manyregions_info.csv"))


var_label(region_info) <- list(
        ROI_name = "Original ROI name that matches file names of ROI parcels", 
        ROI_name_final = "Simplified ROI name",
        ROI_category = "Psychology physics early visual or MD",
        focal_region = "Focal region in analyses?",
        manyregions_region = "Included in regions involving many ROIs?",
        old_ROI = "Old ROI that was generated due to mistake in analysis? Included for transparency"
)


metadata(region_info)$name <- "Region info, Experiment 1"
metadata(region_info)$description <- "Region information for the manuscript entitled 'Violations of physical and psychological expectations in the human adult brain' by Liu et al."
metadata(region_info)$datePublished <- "2023-08-21"
metadata(region_info)$creator <- list(
      "@type" = "Person",
      givenName = "Shari", familyName = "Liu",
      email = "shariliu@jhu.edu", 
      affiliation = list("@type" = "Organization",
        name = "Johns Hopkins University, Baltimore, MD, USA"))
metadata(region_info)$citation <- "Liu, S., Lydic, K., Mei, L., & Saxe, R. (2023, preprint). Violations of physical and psychological expectations in the human adult brain."
metadata(region_info)$temporalCoverage <- "2023" 
```

```{r codebook_3}
codebook(region_info)
```
