---
title: "Violations of physical and psychological expectations in the human adult brain - Compute and visualize visual features across both experiments"
author: "Shari Liu"
date: '2023-08-02'
output:
  html_document:
    code_folding: show
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: yes
    theme: spacelab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
pacman::p_load(tidyverse,
               conflicted,
               cowplot,
               patchwork,
               cluster,
               corrplot,
               pheatmap,
               here,
               vroom,
               R.matlab,
               readr)

conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("rename", "dplyr")
conflict_prefer("summarise", "dplyr")
conflict_prefer("lmer", "lmerTest")
conflict_prefer("here", "here")

source(here("helper_funs.R"))

sessionInfo()

```

## Overview
This script organizes video-level stimulus features across the 96 videos from Experiment 2. The features are: low and high spatial frequency, rectilinearity, curvilinearity, contrast, luminance, and motion. The scripts for calcualting the features themselves can be found at the path `vis_statistics`. Here we compile these data, visualize them, and prepare RDMs / pairwise distances across the main conditions of the experiment, which are: solidity-exp, solidity-unexp, permanence-exp, permanence-unexp (all from the physical domain), goal-exp, goal-unexp, and efficiency-exp, efficiency-unexp (all from psychological domain). We also have, as exploratory trials, videos that cross domains: agentsolidity-exp, agentsolidity-unexp, inferconstraint-exp, and inferconstraint-unexp.

```{r}
# spf.files <- list.files(
#   here("vis_statistics/spatial_freq/output"),
#   pattern = ".mat$",
#   recursive = TRUE,
#   full.names = TRUE
# )
# 
# sf <- data.frame()
# 
# for (file in spf.files) {
#   curmat <- readMat(file)
#   curhsf <- mean(as.vector(curmat$vids.high), na.rm = TRUE)
#   curlsf <- mean(as.vector(curmat$vids.low), na.rm = TRUE)
#   video_string <- str_split(file, "/")[[1]][14]
#   videoname.pre <- str_remove(video_string, "sfInfo_")
#   videoname <- str_remove(videoname.pre, ".mat")
#   cur.row <- data.frame(video = videoname,
#                         hsf = curhsf,
#                         lsf = curlsf)
#   sf <- rbind(sf, cur.row)
# }
# 
# View(sf)
# 
# write.csv(sf, "vis_statistics/spatial_freq/output/SF_ALLVIDEOS.csv")
```

```{r}
# curv.files <- list.files(
#   here("vis_statistics/spatial_freq/output"),
#   pattern = ".mat$",
#   recursive = TRUE,
#   full.names = TRUE
# )
# 
# sf <- data.frame()
# 
# for (file in spf.files) {
#   curmat <- readMat(file)
#   curhsf <- mean(as.vector(curmat$vids.high), na.rm = TRUE)
#   curlsf <- mean(as.vector(curmat$vids.low), na.rm = TRUE)
#   video_string <- str_split(file, "/")[[1]][14]
#   videoname.pre <- str_remove(video_string, "sfInfo_")
#   videoname <- str_remove(videoname.pre, ".mat")
#   cur.row <- data.frame(video = videoname,
#                         hsf = curhsf,
#                         lsf = curlsf)
#   sf <- rbind(sf, cur.row)
# }
# 
# View(sf)
# 
# write.csv(sf, "vis_statistics/spatial_freq/output/SF_ALLVIDEOS.csv")
```

# (1) Read in features


```{r}
# read in data, and z score

contrast <-
  read.csv(here(
    "vis_statistics/luminance_contrast/outputs/CONTRAST_ALL_VIDEOS.csv"
  )) %>%
  mutate(metric = "iqr_contrast") %>%
  rename(value = iqr_contrast) %>%
  mutate(normalized_value = scale(value))

luminance <-
  read.csv(here(
    "vis_statistics/luminance_contrast/outputs/LUMINANCE_ALL_VIDEOS.csv"
  )) %>%
  mutate(metric = "mean_luminance") %>%
  rename(value = mean_luminance) %>%
  mutate(normalized_value = scale(value))

motion <-
  read.csv(here("vis_statistics/motion/MOTION_INFO_ALL-VIDEOS.csv")) %>%
  separate(
    col = video,
    sep = "_",
    into = c("domain", "scenario_group", "scenario_specific", "event"),
    remove = FALSE
  ) %>%
  mutate(metric = "mean_motion") %>%
  rename(value = mean_ME) %>%
  mutate(normalized_value = scale(value))


sp_freq.wide <-
  read.csv(here("vis_statistics/spatial_freq/output/SF_ALLVIDEOS.csv")) %>%
  separate(
    col = video,
    sep = "_",
    into = c("domain", "scenario_group", "scenario_specific", "event"),
    remove = FALSE
  ) 

sp_freq <- sp_freq.wide %>%
  gather("metric", "value", hsf:lsf) %>%
  group_by(metric) %>%
  mutate(normalized_value = scale(value)) %>%
  ungroup() %>%
  select(-X)

sp_freq$metric <- as.factor(sp_freq$metric)
levels(sp_freq$metric) <- c("mean_hsf", "mean_lsf")

curv_rect.wide <-
  read.csv(here("vis_statistics/curvrect_video_means.csv")) %>%
  separate(
    col = video,
    sep = "_",
    into = c("domain", "scenario_group", "scenario_specific", "event"),
    remove = FALSE
  ) %>%
  relocate(c("rect_means", "curv_means"), .after = last_col())

curv_rect <- curv_rect.wide %>%
  gather("metric", "value", rect_means:curv_means) %>%
  group_by(metric) %>%
  mutate(normalized_value = scale(value)) %>%
  ungroup()

curv_rect$metric <- as.factor(curv_rect$metric)
levels(curv_rect$metric) <- c("mean_curv", "mean_rect")

```

```{r}
# now that all the dfs have the same col names, bind them together, filter videos based on what actually appeared in either experiment 1 or 2
metrics.prelim <-
  rbind(contrast, luminance, motion, sp_freq, curv_rect) %>%
  mutate(in_exp1 = case_when(str_detect(video, "exp1") ~ TRUE,
                             TRUE ~ FALSE)) %>%
  mutate(in_exp2 = case_when(str_detect(video, "support") ~ FALSE,
                             TRUE ~ TRUE)) %>%
  filter(str_detect(video, "infer-constraint-3.1_trial2", negate = TRUE)) %>%
  filter(str_detect(video, "infer-constraint-3.1_trial19", negate = TRUE)) %>%
  filter(str_detect(video, "agent-solidity-2.5_trial15", negate = TRUE)) %>%
  filter(str_detect(video, "agent-solidity-2.5_trial6", negate = TRUE)) 
```

```{r}
# deal with events with identical test events appropriately.

# first take the trials that have distinct test trials
metrics.minus.identicals <- metrics.prelim %>%
  filter(event != "test") %>%
  filter(!str_detect(event, "fam-")) %>%
  mutate(event_orig = event) %>%
  mutate(identical_test = FALSE)

# take the test event, make it count towards unexpected event estimate
identical.tests.unexp <- metrics.prelim %>% filter(event == "test") %>%
  rename(event_orig = event) %>%
  mutate(event = "unexp") %>%
  mutate(identical_test = TRUE)

# take the test event, make it count towards expected event estimate
identical.tests.exp <- metrics.prelim %>% filter(event == "test") %>%
  rename(event_orig = event) %>%
  mutate(event = "exp") %>%
  mutate(identical_test = TRUE)

# take the fam-exp and fam-unexp events, and just change them to the type "fam"
identical.tests.fam <- metrics.prelim %>% filter(str_detect(event, "fam-")) %>%
  rename(event_orig = event) %>%
  mutate(event = "fam") %>%
  mutate(identical_test = TRUE)

# now bind all the rows together..
metrics.full <-
  rbind(
    metrics.minus.identicals,
    identical.tests.fam,
    identical.tests.unexp,
    identical.tests.exp
  ) %>%  
  
  # make task names
  mutate(
    task = case_when(
      str_detect(scenario_group, "infer-constraint") ~ "infer-constraint",
      str_detect(scenario_group, "agent-solidity") ~ "agent-solidity",
      str_detect(scenario_group, "solidity") ~ "solidity",
      str_detect(scenario_group, "permanence") ~ "permanence",
      str_detect(scenario_group, "support") ~ "support",
      str_detect(scenario_group, "efficiency") ~ "efficiency",
      str_detect(scenario_group, "goal") ~ "goal"
    )
  )  %>%
  
  # change psych-physics label to "both" to match ROI results
  mutate(domain = case_when(domain == "physics-psychology" ~ "both",
                            TRUE ~ domain)) %>%
  
  unite("video_group", c("domain", "task", "scenario_group", "scenario_specific"), remove = FALSE) 


unique(sort(metrics.full$video_group))
str(metrics.full)
# write_rds(metrics.full, here("outputs/visual_statistics/vis_features_pervideo.Rds"))
```

```{r}
metrics.full.unnormalized <- metrics.full %>%
  select(-contains("normalized_value")) %>%
  pivot_wider(names_from = metric, 
              values_from = value)

metrics.full.normalized <- metrics.full %>%
  select(-value) %>%
  pivot_wider(names_from = metric, 
              values_from = normalized_value,
              names_prefix = "normalized_")

visual_statistics_full <-
  full_join(metrics.full.unnormalized, metrics.full.normalized) %>%
  separate(
    col = video,
    sep = "_",
    into = c("video_domain", "video_scenario_group", "video_scenario_specific", "video_event"),
    remove = TRUE
  ) %>%
  mutate(video_domain = case_when(video_domain == "physics-psychology" ~ "both",
                                  TRUE ~ video_domain)) %>%
  unite("vis_statistics_video_group", c("video_domain", "video_scenario_group", "video_scenario_specific"), remove = TRUE)

# write.csv(visual_statistics_full, here("outputs/visual_statistics/visual_statistics_full_new.csv"))
```

### Tidy up z scores per experiment
```{r, eval = FALSE}
all_videos <- read.csv(here("outputs/visual_statistics/visual_statistics_full_new.csv")) %>%
  select(-contains("normalized"))

str(all_videos)

visual_statistics_exp1 <- all_videos %>%
  filter(in_exp1 == TRUE) %>%
  gather("metric", "value", iqr_contrast:mean_curv) %>%
  group_by(metric) %>%
  mutate(normalized_value = scale(value)) %>%
  ungroup()

# write.csv(visual_statistics_exp1, here("outputs/visual_statistics/visual_statistics_exp1_new.csv"))

visual_statistics_exp2 <- all_videos %>%
  filter(in_exp2 == TRUE) %>%
  gather("metric", "value", iqr_contrast:mean_curv) %>%
  group_by(metric) %>%
  mutate(normalized_value = scale(value)) %>%
  ungroup()

# write.csv(visual_statistics_exp2, here("outputs/visual_statistics/visual_statistics_exp2_new.csv"))

```


# (2) Visualize per video

```{r}
metrics.full <- readRDS(here("outputs/visual_statistics/vis_features_pervideo.Rds"))

# remove fam events, and support events (only in exp 1)
metrics <- metrics.full %>%
  filter(task != "support",
         event != "fam")

metrics_by_event <- ggplot(data = metrics %>% filter(domain != "both"),
                       aes(
                         x = event,
                         y = normalized_value,
                         # label = video,
                         fill = event
                       )) +
  geom_boxplot(position = position_dodge(width = 0.8)) +
  geom_point(position = position_dodge(width = 0.8)) +
  ylab("Normalized measure per video") +
  facet_wrap(~metric + domain, nrow = 1) +
  theme_cowplot(12) +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 0.5,
    hjust = 1
  ))

```



```{r}
metrics_by_domain <- ggplot(data = metrics,
                       aes(
                         x = domain,
                         y = normalized_value,
                         # label = video,
                         fill = domain
                       )) +
  geom_boxplot(position = position_dodge(width = 0.8)) +
  geom_point(position = position_dodge(width = 0.8)) +
  ylab("Normalized measure per video") +
  facet_wrap(~metric, nrow = 1) +
  theme_cowplot(12) +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = 0.5,
    hjust = 1
  ))
```

Eexpected and unexpected movies are about equal, on average, with respect to all of these features. However, these features vary by domain.

```{r fig.height = 14}
metrics_by_event / metrics_by_domain + plot_annotation(tag_levels = 'A')
```

