---
title: "Violations of physical and psychological expectations in the human adult brain - Experiment 2 Multivariate Analysis"
author: "Shari Liu"
date: '2023-08-03'
output:
  html_document:
    code_folding: hide
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: yes
    theme: spacelab
---
# Overview

This script:

Part 1: visualizes and analyzes the within vs between multivariate patterns in 8 focal regions (left and right SMG, left and right STS, left and right V1, bilateral APC and RFC), along the following boundaries:

- event within domain
- event across domain
- domain within event
- domain across event

Part 2: Performs a region by region MVPA effect size analysis over domain-specific and domain-general regions.

Part 3: Same as part 1, but for other, non-focal ROIs

All instances of `write_rds` and similar have been commented out to avoid writing over existing files. Uncomment those statements in order to reproduce these steps and save (new) outputs.

```{r setup}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
pacman::p_load(tidyverse,
               conflicted,
               cowplot,
               here,
               effsize,
               ggrepel,
               patchwork,
               ggpubr,
               boot,
               nptest,
               boot.pval,
               doMC
)

conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("rename", "dplyr")
conflict_prefer("arrange", "dplyr")

conflict_prefer("summarise", "dplyr")
conflict_prefer("lmer", "lmerTest")
conflict_prefer("here", "here")

source(here("helper_funs.R"))

sessionInfo()
```

First we set up the data.

```{r}
MVPA_processed_distances <- readRDS(here("outputs/multivariate_data/study2_MVPA_processed_distances_top100_runs12.Rds")) %>%
  filter(
         # row_domain != "both",
         # column_domain != "both",
         row_event != "fam",
         column_event != "fam",
         same_run == 0)

# repeat the following processing steps w this df to get results including distances within runs (exploratory)
MVPA_processed_distances_within_runs_only <- readRDS(here("outputs/multivariate_data/study2_MVPA_processed_distances_top100_runs12.Rds")) %>%
  filter(
         # row_domain != "both",
         # column_domain != "both",
         row_event != "fam",
         same_run == 1,
         column_event != "fam")
```

# SETUP: Summarize between vs within distances

For all the steps below, enter either dataset from above to compute the distances, either only between runs (pre-registered) or only within runs (exploratory).

## (1) Events Across Domains

```{r, eval = FALSE}
event.across.domain.summarylong <- MVPA_processed_distances %>%
  filter(pair_label_event_across_domains != "drop_domain") %>%
  group_by(distance_metric,
           subj,
           ROI_name_final,
           pair_label_event_across_domains) %>%
  summarise(mean_dist = mean(dist))

event.across.domain.summarywide <-
  event.across.domain.summarylong %>%
  pivot_wider(
    id_cols = c(subj, ROI_name_final, distance_metric),
    names_from = pair_label_event_across_domains,
    values_from = mean_dist
  ) %>%
  mutate(diff = between - within,
         category = "event_across_domain")

results1_event.across.domain <- event.across.domain.summarywide %>% 
  group_by(distance_metric, ROI_name_final, category) %>%
  summarise(V = wilcox.test(diff, alternative = "greater", mu = 0)$statistic,
            p = wilcox.test(diff, alternative = "greater", mu = 0)$p.value,
            z = qnorm(p/2),
            r = abs(z/sqrt(32))) 
```

## (2) Domains Across Events

```{r, eval = FALSE}
domain.across.event.summarylong <- MVPA_processed_distances %>%
  filter(pair_label_domains_across_events != "drop_event") %>%
  group_by(distance_metric,
           subj,
           ROI_name_final,
           pair_label_domains_across_events) %>%
  summarise(mean_dist = mean(dist))

domain.across.event.summarywide <-
  domain.across.event.summarylong %>%
  pivot_wider(
    id_cols = c(subj, ROI_name_final, distance_metric),
    names_from = pair_label_domains_across_events,
    values_from = mean_dist
  ) %>%
  mutate(diff = between - within,
         category = "domain_across_event")


results2_domain.across.event <- domain.across.event.summarywide %>% 
  group_by(distance_metric, ROI_name_final, category) %>%
  summarise(V = wilcox.test(diff, alternative = "greater", mu = 0)$statistic,
            p = wilcox.test(diff, alternative = "greater", mu = 0)$p.value,
            z = qnorm(p/2),
            r = abs(z/sqrt(32))) 
```

## (3) Events within domains

```{r, eval = FALSE}

event.within.domain.summarylong <- MVPA_processed_distances %>%
  filter(pair_label_event_within_domain != "drop_domain") %>%
  group_by(distance_metric,
           subj,
           ROI_name_final,
           pair_label_event_within_domain) %>%
  summarise(mean_dist = mean(dist))

event.within.domain.summarywide <-
  event.within.domain.summarylong %>%
  pivot_wider(
    id_cols = c(subj, ROI_name_final, distance_metric),
    names_from = pair_label_event_within_domain,
    values_from = mean_dist
  ) %>%
  mutate(diff = between - within)

event.within.domain.perdomain.summarylong <-
  MVPA_processed_distances %>%
  filter(pair_label_event_within_domain != "drop_domain") %>%
  group_by(distance_metric,
           subj,
           ROI_name_final,
           same_domain,
           pair_label_event_within_domain) %>%
  summarise(mean_dist = mean(dist))


event.within.domain.perdomain.summarywide <-
  event.within.domain.perdomain.summarylong %>%
  pivot_wider(
    id_cols = c(subj, ROI_name_final, distance_metric, same_domain),
    names_from = pair_label_event_within_domain,
    values_from = mean_dist
  ) %>%
  mutate(diff = between - within,
         category = "event_within_domain")

results3_event.within.domain <- event.within.domain.perdomain.summarywide %>% 
  group_by(distance_metric, same_domain, ROI_name_final, category) %>%
  summarise(V = wilcox.test(diff, alternative = "greater", mu = 0)$statistic,
            p = wilcox.test(diff, alternative = "greater", mu = 0)$p.value,
            z = qnorm(p/2),
            r = abs(z/sqrt(32))) 
```

## (4) Domains within events

```{r, eval = FALSE}

domain.within.event.summarylong <- MVPA_processed_distances %>%
  filter(
      pair_label_domain_within_event != "drop_event"
  ) %>%
  group_by(distance_metric, subj, ROI_name_final, pair_label_domain_within_event) %>%
  summarise(mean_dist = mean(dist))

domain.within.event.summarywide <-
  domain.within.event.summarylong %>%
  pivot_wider(
    id_cols = c(subj, ROI_name_final, distance_metric),
    names_from = pair_label_domain_within_event,
    values_from = mean_dist
  ) %>%
  mutate(diff = between - within)

domain.within.event.perevent.summarylong <-
  MVPA_processed_distances %>%
  filter(
      pair_label_domain_within_event != "drop_event"
  ) %>%
  group_by(distance_metric,
           subj,
           ROI_name_final,
           same_event,
           pair_label_domain_within_event) %>%
  summarise(mean_dist = mean(dist))

domain.within.event.perevent.summarywide <-
  domain.within.event.perevent.summarylong %>%
  pivot_wider(
    id_cols = c(subj, ROI_name_final, distance_metric, same_event),
    names_from = pair_label_domain_within_event,
    values_from = mean_dist
  ) %>%
  mutate(diff = between - within,
         category = "domain_within_event")


results4_domain.within.event <- domain.within.event.perevent.summarywide %>% 
  group_by(distance_metric, same_event, ROI_name_final, category) %>%
  summarise(V = wilcox.test(diff, alternative = "greater", mu = 0)$statistic,
            p = wilcox.test(diff, alternative = "greater", mu = 0)$p.value,
            z = qnorm(p/2),
            r = abs(z/sqrt(32))) 
```

## Combining MVPA results

```{r, eval = FALSE}

MVPA_results0 <-
  rbind(
    results1_event.across.domain,
    results2_domain.across.event,
    results3_event.within.domain,  ## only relevant for between runs
    results4_domain.within.event
  ) %>%
  mutate(p_tails = "one",
         H0_mu = 0,
         H1 = "greater") %>%
  as.data.frame()

region_info <- read.csv(here("input_data/manyregions_info.csv"))

MVPA_results <- full_join(MVPA_results0, region_info) 

MVPA_results_out <- MVPA_results %>%
  mutate(p = round(p, digits = 3)) %>%
  mutate(star = as.factor(case_when(p< .001 ~ "***",
                        p < .01 ~ "**",
                        p < .05 ~ "*",
                        p < .1 ~ "~",
                        TRUE ~ " "))) %>%
  mutate(test = "one-tailed Wilcoxon signed rank test against mu = 0")

MVPA_results_out$ROI_category <- factor(MVPA_results_out$ROI_category, levels = c("physics", "psychology", "MD", "early_visual"))
# saveRDS(MVPA_results_out, here("outputs/multivariate_results/study2_MVPA_results_exploratory_across_runs12_including_psych_env.Rds"))
```

```{r, eval = FALSE}
MVPA_results_persubject0 <-
  rbind(
    event.across.domain.summarywide,
    domain.across.event.summarywide,
    event.within.domain.perdomain.summarywide,  ## only relevant for between runs
    domain.within.event.perevent.summarywide
  ) %>%
  as.data.frame()

MVPA_results_persubject <- full_join(MVPA_results_persubject0, region_info)
MVPA_results_persubject$ROI_category <- factor(MVPA_results_persubject$ROI_category, levels = c("physics", "psychology", "MD", "early_visual"))

# saveRDS(MVPA_results_persubject, here("outputs/multivariate_results/study2_MVPA_results_exploratory_across_runs12_including_psych_env_persubject.Rds"))

```

## Retain + export within and between distances for visualization, and join with noise ceiling

```{r}
euclidean_noise_ceiling <- readRDS(here("outputs/multivariate_results/study2_MVPA_noiseceiling_withinrun_perROI.Rds")) %>%
  filter(cor_metric == "euclidean") %>%
  select(-cor_metric) 
```

```{r, eval = FALSE}
MVPA_results_within_between_separate_prelim <-
  rbind(
    domain.within.event.summarylong,
    event.within.domain.summarylong,
    domain.within.event.perevent.summarylong,
    event.within.domain.perdomain.summarylong,
    domain.across.event.summarylong,
    event.across.domain.summarylong
  )

MVPA_results_withinrun_prelim2 <- left_join(MVPA_results_within_between_separate_prelim, euclidean_noise_ceiling)

MVPA_results_withinrun_final <- left_join(MVPA_results_withinrun_prelim2, region_info)

MVPA_results_withinrun_final$ROI_category <-
  factor(
    MVPA_results_withinrun_final$ROI_category,
    levels = c("physics", "psychology", "MD", "early_visual")
  )
# saveRDS(MVPA_results_withinrun_final, here("outputs/multivariate_results/study2_MVPA_results_withinruns12_with_noise_ceiling.Rds"))

```


# PART 1 (Confirmatory): Focal regions

```{r}
MVPA_results_focal <-
  readRDS(here("outputs/multivariate_results/study2_MVPA_results_betweenruns12.Rds")) %>%
  filter(focal_region == 1,
         distance_metric == "euclidean")

MVPA_results_focal_persubject <- 
  readRDS(here("outputs/multivariate_results/study2_MVPA_results_betweenruns12_persubject.Rds")) %>%
  filter(focal_region == 1,
         distance_metric == "euclidean")

MVPA_results_focal %>%
  group_by(ROI_name_final, category) %>%
  summarise(n = n())

MVPA_results_focal_persubject %>%
  group_by(ROI_name_final, category) %>%
  summarise(n = n())

DT::datatable(dplyr::arrange(MVPA_results_focal, category),  options = list(scrollX = TRUE))

```

```{r}

plot_multivariate <- function(dataframe, dataframe_persubject, category_label, facet_label) {
  plot <-
    ggplot(
      dataframe_persubject %>% filter(
        category == {{category_label}},
        distance_metric == "euclidean"
      ) %>%
        arrange(ROI_category),
      aes(x = ROI_name_final, y = diff, fill = ROI_category)
    ) +
    stat_summary(stat = "mean_se()", geom = "bar") +
    geom_hline(yintercept = 0, linetype = "dotted") +
    stat_summary(
      geom = "errorbar",
      width = .1,
      fun.data = "mean_se",
      colour = "black"
    ) +
    ylab("Between - Within Euclidean Distance") +
    geom_text(
      data = dataframe %>% filter(
        category == {{category_label}},
        distance_metric == "euclidean"
      ),
      mapping = aes(label = star, x = ROI_name_final, y = -10),
      size = 7,
      colour = "red",
      family = "mono",
      # inherit.aes = FALSE
    ) +
    geom_point(alpha = .2) +
    theme_cowplot(10) +
    scale_fill_manual(values = c("#4894ff", "#f71d00", "#f8bf00", "#fb00d3")) +
    coord_flip() +
    ggtitle(paste0("Category boundary: ", category_label))
  
  if (!is.na(facet_label)) {
    return(plot + facet_wrap({{facet_label}}))
  }
  else {
    return(plot)
  }
}

```

```{r}
plot_multivariate(MVPA_results_focal %>% filter(focal_region == 1, distance_metric == "euclidean"), MVPA_results_focal_persubject  %>% filter(focal_region == 1, distance_metric == "euclidean"), "domain_across_event", NA)
plot_multivariate(MVPA_results_focal %>% filter(focal_region == 1, distance_metric == "euclidean"), MVPA_results_focal_persubject  %>% filter(focal_region == 1, distance_metric == "euclidean"), "event_across_domain", NA)
plot_multivariate(MVPA_results_focal %>% filter(focal_region == 1), MVPA_results_focal_persubject  %>% filter(focal_region == 1), "domain_within_event", "same_event")
plot_multivariate(MVPA_results_focal %>% filter(focal_region == 1), MVPA_results_focal_persubject  %>% filter(focal_region == 1), "event_within_domain", "same_domain")
```




```{r}
MVPA_results_within_between_separate_final <- read_rds( here("outputs/multivariate_results/study2_MVPA_results_betweenruns12_with_noise_ceiling.Rds"))


MVPA_focal_domainplot <-
  ggplot(
    MVPA_results_within_between_separate_final %>%
      filter(
        !is.na(pair_label_domains_across_events),
        distance_metric == "euclidean",
        focal_region == 1
      ),
    aes(pair_label_domains_across_events, mean_dist, fill = ROI_category)
  ) +
  # geom_boxplot() +
  stat_summary(stat = "mean_se()",
               geom = "bar",
               colour = "black") +
  stat_summary(stat = "mean_se()", geom = "errorbar", width = .2) +
  geom_point(alpha = .2) +
  scale_fill_manual(values = c("#4894ff", "#f71d00", "#f8bf00", "#fb00d3")) +
  facet_wrap(
    ~ factor(
      ROI_name_final,
      levels = c(
        "superiortemporal_L",
        "superiortemporal_R",
        "supramarginal_L",
        "supramarginal_R",
        "antParietal_bilateral",
        "precentral_inferiorfrontal_R",
        "V1_bilateral",
        "MT_bilateral"
      )
    ),
    labeller = labeller(ROI_name_final = label_wrap_gen(width = 10, multi_line = TRUE)),
    nrow = 2
  ) +
  xlab("Domains Across Events Category Boundary") +
  ylab("Euclidean Distance") +
  geom_hline(
    data = euclidean_noise_ceiling %>% filter(focal_region == 1),
    aes(
      yintercept = noiseceiling_upper,
      size = 1,
      alpha = 0.5
    )
  )

MVPA_focal_eventplot <-
  ggplot(
    MVPA_results_within_between_separate_final %>%
      filter(
        !is.na(pair_label_event_across_domains),
        distance_metric == "euclidean",
        focal_region == 1
      ),
    aes(pair_label_event_across_domains, mean_dist, fill = ROI_category)
  ) +
  # geom_boxplot() +
  stat_summary(stat = "mean_se()",
               geom = "bar",
               colour = "black") +
  stat_summary(stat = "mean_se()", geom = "errorbar", width = .2) +
  geom_point(alpha = .2) +
  xlab("Events Across Domains Category Boundary") +
  ylab("Euclidean Distance") +
  scale_fill_manual(values = c("#4894ff", "#f71d00", "#f8bf00", "#fb00d3")) +
  facet_wrap( ~ factor(
    ROI_name_final,
    levels = c(
      "superiortemporal_L",
      "superiortemporal_R",
      "supramarginal_L",
      "supramarginal_R",
      "antParietal_bilateral",
      "precentral_inferiorfrontal_R",
      "V1_bilateral",
      "MT_bilateral"
    )
  ), nrow = 2) +
  geom_hline(
    aes(
      yintercept = noiseceiling_upper,
      size = 1,
      alpha = 0.5
    ))
```


```{r}
MVPA_results_withinrun_final <- readRDS(here("outputs/multivariate_results/study2_MVPA_results_withinruns12_with_noise_ceiling.Rds"))

MVPA_focal_eventplot <-
  ggplot(
    MVPA_results_withinrun_final %>%
      filter(
        !is.na(pair_label_event_across_domains),
        distance_metric == "euclidean",
        focal_region == 1
      ),
    aes(pair_label_event_across_domains, mean_dist, fill = ROI_category)
  ) +
  # geom_boxplot() +
  stat_summary(stat = "mean_se()",
               geom = "bar",
               colour = "black") +
  stat_summary(stat = "mean_se()", geom = "errorbar", width = .2) +
  geom_point(alpha = .2) +
  xlab("Events Across Domains Category Boundary") +
  ylab("Euclidean Distance") +
  scale_fill_manual(values = c("#4894ff", "#f71d00", "#f8bf00", "#fb00d3")) +
  facet_wrap( ~ factor(
    ROI_name_final,
    levels = c(
      "superiortemporal_L",
      "superiortemporal_R",
      "supramarginal_L",
      "supramarginal_R",
      "antParietal_bilateral",
      "precentral_inferiorfrontal_R",
      "V1_bilateral",
      "MT_bilateral"
    )
  ), nrow = 2) +
  coord_cartesian(ylim = c(0, 75)) +
  geom_hline(
    aes(
      yintercept = noiseceiling_upper,
      size = 1,
      alpha = 0.5
    ))
  
```

```{r}
MVPA_focal_domainplot + MVPA_focal_eventplot
```

# PART 2 (Confirmatory): Region by Region Effect Size

## Domain specific regions

```{r}
DS_results <- readRDS(here("outputs/multivariate_results/study2_MVPA_results_betweenruns12.Rds")) %>%
  filter(distance_metric == "euclidean_zscored") %>%
  filter(manyregions_region == 1) %>%
  filter(ROI_category == "psychology" | ROI_category == "physics") %>%
  pivot_wider(id_cols = c(ROI_name_final, ROI_category), names_from = c(category, same_domain, same_event), values_from = r) %>%
  mutate(domain = "specific")

colnames(DS_results) <- gsub("_NA","",colnames(DS_results))

DS_results_z <- DS_results %>%
  mutate_at(c("event_within_domain_physics", 
              "event_within_domain_psychology",
              "domain_within_event_exp",
              "domain_within_event_unexp"), scale)


DS_results_sqrt <- DS_results %>%
  mutate_at(c("event_within_domain_physics", 
              "event_within_domain_psychology",
              "domain_within_event_exp",
              "domain_within_event_unexp"), sqrt)


DS_events_within_domains <-
  ggplot(data = DS_results,
         aes(event_within_domain_psychology, event_within_domain_physics)) +
  geom_smooth(method = "glm", colour = "black") +
  geom_point(aes(colour = ROI_category), size = 3) +
  ylab("Effect size (r), Events within Domains, Physics") +
  xlab("Effect size (r), Events within Domains, Psychology") +
  # coord_cartesian(ylim = c(-1, 1),
  #                 xlim = c(-1, 1)) +
  geom_text_repel(aes(label = ROI_name_final), size = 3) +
  theme_cowplot(10) +
  scale_colour_manual(values = c("#4894ff", "#f71d00")) +
  ggtitle(label = "MVPA effect sizes per ROI, \nevents within domains, z-scored")

# f71d00 red
# 4894ff blue
# f8bf00 yellow
# fb00d3 pink

DS_domains_within_events <-
  ggplot(data = DS_results,
         aes(
           domain_within_event_exp,
           domain_within_event_unexp
         )) +
  geom_smooth(method = "glm", colour = "black") +
  geom_point(aes(colour = ROI_category), size = 3) +
  xlab("Effect size (r), Domains within Events, Expected") +
  ylab("Effect size (r), Domains within Events, Unexpected") +
  # coord_cartesian(ylim = c(0, 1),
  #                 xlim = c(0, 1)) +
  geom_text_repel(aes(label = ROI_name_final), size = 3) +
  theme_cowplot(10) +
  scale_colour_manual(values = c("#4894ff", "#f71d00")) +
  ggtitle(label = "MVPA effect sizes per ROI, \ndomains within events, z-scored")

```

```{r out.width="100%"}
DS_events_within_domains + DS_domains_within_events
```

## Domain general regions

```{r}
DG_results <- readRDS(here("outputs/multivariate_results/study2_MVPA_results_betweenruns12.Rds")) %>%
  filter(distance_metric == "euclidean_zscored") %>%
  filter(manyregions_region == 1) %>%
  filter(ROI_category == "MD" | ROI_category == "early_visual") %>%
  filter(!str_detect(ROI_name_final, "_bilateral")) %>% # use L/R regions, bilateral was for focal region analysis
  pivot_wider(id_cols = c(ROI_name_final, ROI_category), names_from = c(category, same_domain, same_event), values_from = r) %>%
  mutate(domain = "general")

colnames(DG_results) <- gsub("_NA","",colnames(DG_results))

DG_results_z <- DG_results %>%
  mutate_at(c("event_within_domain_physics", 
              "event_within_domain_psychology",
              "domain_within_event_exp",
              "domain_within_event_unexp"), scale)

DG_results_sqrt <- DG_results %>%
  mutate_at(c("event_within_domain_physics", 
              "event_within_domain_psychology",
              "domain_within_event_exp",
              "domain_within_event_unexp"), sqrt)

DG_events_within_domains <-
  ggplot(data = DG_results,
         aes(event_within_domain_psychology, event_within_domain_physics)) +
  geom_smooth(method = "glm", colour = "black") +
  geom_point(aes(colour = ROI_category), size = 3) +
  ylab("Effect size (r), Events within Domains, Physics") +
  xlab("Effect size (r), Events within Domains, Psychology") +
  # coord_cartesian(ylim = c(0, 1),
                  # xlim = c(0, 1)) +
  geom_text_repel(aes(label = ROI_name_final), size = 3) +
  theme_cowplot(10) +
  scale_colour_manual(values = c("#f8bf00", "#fb00d3")) +
  ggtitle(label = "MVPA effect sizes per ROI, \nevents within domains, z-scored")

DG_domains_within_events <-
  ggplot(data = DG_results,
         aes(
           domain_within_event_exp,
           domain_within_event_unexp
         )) +
  geom_smooth(method = "glm", colour = "black") +
  geom_point(aes(colour = ROI_category), size = 3) +
  xlab("Effect size (r), Domains within Events, Expected") +
  ylab("Effect size (r), Domains within Events, Unexpected") +
  # coord_cartesian(ylim = c(0, 1),
  #                 xlim = c(0, 1)) +
  geom_text_repel(aes(label = ROI_name_final), size = 3) +
  theme_cowplot(10) +
  scale_colour_manual(values = c("#f8bf00", "#fb00d3")) +
  ggtitle(label = "MVPA effect sizes per ROI, \ndomains within events, z-scored")

```

```{r out.width="100%"}
DG_events_within_domains + DG_domains_within_events
```

## Statistics

```{r}
# instead of testing whether the linear relationship between x and y is 0, 
# we test for independence instead. H0 is that x and y are independent; F_{XY}(x,y) = F_X(x) F_Y(y).
observed_cors_ind <- rbind(DS_results, DG_results) %>%
  group_by(domain) %>%
  summarise(
    cor_domain_within_event =
      np.cor.test(
        domain_within_event_exp,
        domain_within_event_unexp,
        alternative = "greater",
        independent = TRUE
      )$estimate,
    
    p_domain_within_event =
      np.cor.test(
        domain_within_event_exp,
        domain_within_event_unexp,
        alternative = "greater",
        independent = TRUE
      )$p.value,
    
    cor_event_within_domain =
      np.cor.test(
        DG_results$event_within_domain_psychology,
        DG_results$event_within_domain_physics,
        alternative = "greater",
        independent = TRUE
      )$estimate,
    
    p_event_within_domain =
      np.cor.test(
        DG_results$event_within_domain_psychology,
        DG_results$event_within_domain_physics,
        alternative = "greater",
        independent = TRUE
      )$p.value
  )

observed_cors_ind
# write_rds(observed_cors_ind, path = here("outputs/multivariate_results/study2_MVPA_manyregions_observed_cor.Rds"))

```

```{r}

set.seed(2020)
## First define a function to work out the difference of corrs:
diff_corr <- function(data, indices) {
  data <- data[indices,]
  cor1 <-
    np.cor.test(data$domain_within_event_exp,
                data$domain_within_event_unexp,
                alternative = "greater",
                independent = TRUE,
                parallel = TRUE)$estimate
  cor2 <-
    np.cor.test(
      data$event_within_domain_psychology,
      data$event_within_domain_physics,
      alternative = "greater",
      independent = TRUE,
      parallel = TRUE)$estimate

    return(cor1 - cor2)
}


```

### Domain specific

```{r}
doMC::registerDoMC(cores = 2)  # for running in parallel

# Then apply a bootstrap procedure with 4000 draws (uncomment to reproduce):
# res_boot_DS <- boot(
#   data = DS_results,
#   R = 4000,
#   statistic = diff_corr,
#   stype = "i"
# )

# saveRDS(res_boot_DS, here("outputs/multivariate_results/study2_MVPA_dsregions_4000perms_confirmatory.Rds"))

res_boot_DS <- read_rds(here("outputs/multivariate_results/study2_MVPA_dsregions_4000perms_confirmatory.Rds"))

## Retrieve the empirical 95% confidence interval:
ds_results <- append(boot.ci(res_boot_DS, type = "perc", conf = 0.95),boot.pval(res_boot_DS))

# saveRDS(ds_results, here("outputs/multivariate_results/study2_MVPA_dsregions_summary.Rds"))

```

### Domain general

```{r}
## Then apply a bootstrap procedure with 4000 draws (uncomment to reproduce):
# res_boot_DG <- boot(data = DG_results,
#                  R = 4000,
#                  statistic = diff_corr,
#                  stype = "i")

# saveRDS(res_boot_DG, here("outputs/multivariate_results/study2_MVPA_dgregions_4000perms_confirmatory.Rds"))
res_boot_DG <- readRDS(here("outputs/multivariate_results/study2_MVPA_dgregions_4000perms_confirmatory.Rds"))

plot(res_boot_DG)

## Retrieve the empirical 95% confidence interval (adjusted to 90% because of one-tailed prediction):

dg_results <- append(boot.ci(res_boot_DG, type = "perc", conf = 0.95),boot.pval(res_boot_DG))
saveRDS(dg_results, here("outputs/multivariate_results/study2_MVPA_dgregions_summary.Rds"))

```

# PART 3 (Exploratory): All regions

```{r}
MVPA_results_all <- readRDS(here("outputs/multivariate_results/study2_MVPA_results_betweenruns12.Rds")) %>%
  filter(distance_metric == "euclidean")

MVPA_results_all_persubject <- readRDS(here("outputs/multivariate_results/study2_MVPA_results_betweenruns12_persubject.Rds")) %>%
  filter(distance_metric == "euclidean")

MVPA_results_all %>%
  group_by(ROI_name_final, category) %>%
  summarise(n = n())

MVPA_results_all_persubject %>%
  group_by(ROI_name_final, category) %>%
  summarise(n = n())
```

```{r}

plot_multivariate_all <- function(category_label, facet_label) {
  plot <-
    ggplot(
      MVPA_results_all_persubject %>% filter(
        category == {{category_label}},
        distance_metric == "euclidean"
      ),
      aes(x = ROI_name_final, y = diff, fill = ROI_category)
    ) +
    stat_summary(stat = "mean_se()", geom = "bar") +
    geom_hline(yintercept = 0, linetype = "dotted") +
    stat_summary(
      geom = "errorbar",
      width = .1,
      fun.data = "mean_se",
      colour = "black"
    ) +
    ylab("Between - Within Euclidean Distance") +
    geom_text(
      data = MVPA_results_all %>% filter(
        category == {{category_label}},
        distance_metric == "euclidean"
      ),
      mapping = aes(label = star, x = ROI_name_final, y = -10),
      size = 7,
      colour = "red",
      family = "mono",
      # inherit.aes = FALSE
    ) +
    geom_point(alpha = .2) +
    theme_cowplot(10) +
    scale_fill_manual(values = c("#2eafb9", "#f74d09", "#f2de1e", "#f269f5")) +
    coord_flip() +
    ggtitle(paste0("Category boundary: ", category_label))
  
  if (!is.na(facet_label)) {
    return(plot + facet_wrap(vars(.data[[facet_label]])))
  }
  else {
    return(plot)
  }
}

plot_multivariate_all("domain_across_event", NA)
plot_multivariate_all("event_across_domain", NA)
plot_multivariate_all("domain_within_event", "same_event")
plot_multivariate_all("event_within_domain", "same_domain")
```
