---
title: "5_Validate_Localizers"
author: "Shari Liu"
date: "2023-10-26"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 1, digits = 3)
library(pacman)
pacman::p_load(tidyverse,
               patchwork,
               papaja,
               ggforce,
               conflicted,
               here,
               cowplot)

conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("rename", "dplyr")
conflict_prefer("mutate", "dplyr")
conflict_prefer("summarise", "dplyr")
conflict_prefer("lmer", "lmerTest")
conflict_prefer("here", "here")

source(here("helper_funs.R"))

theme_set(theme_cowplot(10))

sessionInfo()
```


## Overview
As requested by a reviewer, here we conducted a validation of our three localizer tasks in our focal regions.

The logic of this analysis is the following:

- For all subjects that have two runs of data, we used a leave one run out approach to check whether the ROIs reliably respond to the same contrasts they were selected for in held out data
- We first used run 1 to identify the ROI and run 2 to extract the responses using the same contrast.
- We then used run 2 to identify the ROI and run 1 to extract the responses using the same contrast.

Here we will average these responses across folds per subject per ROI, and then plot the responses.

```{r}
localizer_data_init <-
  read.csv(here("input_data/localizer_validation_outputs_Nov07_2023.csv"), header = TRUE) %>%
  rename(ROI_name = roi) 

region_info <- read.csv(here("input_data/manyregions_info.csv")) %>%
  mutate(ROI_name = paste0(ROI_name, "_MNI152Lin2009cAsym_res-02", sep = ""))

localizer_data <- left_join(localizer_data_init, region_info)

localizer_data$ROI_category <- factor(localizer_data$ROI_category, levels=c('physics', 'psychology', 'MD', 'early_visual'))

```

```{r}
localizer_data_avg_fold <- localizer_data %>%
  group_by(subjectID, ROI_name_final, ROI_category, task, extraction_contrast) %>%
  summarise(average_cope_across_folds = mean(mean_topvoxels_extracted_cope))
  
```

```{r}
plot1 <- ggplot(localizer_data_avg_fold, aes(ROI_name_final, average_cope_across_folds, fill = ROI_category)) + 
  geom_boxplot() +
  geom_point(alpha = 0.2) +
  geom_hline(yintercept = 0) + 
  stat_summary(geom = "pointrange", fun.data = "mean_cl_boot", colour = "white") +
  facet_wrap(~ROI_category, scales = "free", nrow = 4) +
  scale_fill_manual(values = c("#4894ff", "#f71d00", "#f8bf00", "#fb00d3")) +
  ylab("Cope from held out data") +
  theme(legend.position = "none")
```

```{r}
ggplot(localizer_data_avg_fold, aes( average_cope_across_folds, fill = ROI_category)) + 
  geom_histogram() +
  facet_wrap(~ROI_category, scales = "free", nrow = 1) +
  scale_fill_manual(values = c("#4894ff", "#f71d00", "#f8bf00", "#fb00d3")) +
  # ylab("Cope from held out data") +
  theme(legend.position = "none")
```


```{r}
localizer_data_byrun <- localizer_data %>%
  select(subjectID, task, ROI_category, ROI_name_final, selection_contrast, extracted_run_number, mean_topvoxels_extracted_cope) %>%
  pivot_wider(id_cols = c(subjectID, task, ROI_category, ROI_name_final, selection_contrast), names_from = "extracted_run_number", values_from = "mean_topvoxels_extracted_cope", names_prefix = "extracted_cope_") 
```


```{r}
reliability <- localizer_data_byrun %>%
  group_by(ROI_name_final) %>%
  summarise(r = cor.test(extracted_cope_run1, extracted_cope_run2, method = "pearson", paired = TRUE, alterative = "greater")$estimate,
            r_p = cor.test(extracted_cope_run1, extracted_cope_run2, method = "pearson", paired = TRUE, alterative = "greater")$p.value,
            tau = cor.test(extracted_cope_run1, extracted_cope_run2, method = "kendall", paired = TRUE, alterative = "greater")$estimate,
            tau_p = cor.test(extracted_cope_run1, extracted_cope_run2, method = "kendall", paired = TRUE, alterative = "greater")$p.value) %>%
 mutate(star = as.factor(case_when(tau_p< .001 ~ "***",
                        tau_p < .01 ~ "**",
                        tau_p < .05 ~ "*",
                        tau_p < .1 ~ "~",
                        TRUE ~ " "))) %>%
  mutate(tau_spearman_brown = (2*tau)/(1+tau))
```

```{r}
plot2<- ggplot(
  localizer_data_byrun,
  aes(extracted_cope_run1, extracted_cope_run2, colour = ROI_category)
) +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0) +
  geom_point() +
  geom_smooth(method = "lm") +
  coord_cartesian(xlim = c(-1, 20), ylim = c(-1, 20)) +
  scale_colour_manual(values = c("#4894ff", "#f71d00", "#f8bf00", "#fb00d3")) +
  facet_wrap( ~ factor(
    ROI_name_final,
    levels = c(
      'supramarginal_L',
      'supramarginal_R',
      'superiortemporal_L',
      'superiortemporal_R',
      'antParietal_bilateral',
      'precentral_inferiorfrontal_R',
      'V1_bilateral',
      'MT_bilateral'
    )
  ), nrow = 4) +
  ylab('Cope value, run 2') +
  xlab('Cope value, run 1') +
  geom_text(
    data = reliability,
    mapping = aes(
      label = paste(star, "τ=", round(tau_spearman_brown, 3)),
      x = 8,
      y = 18
    ),
    size = 4,
    colour = "black",
    # family = "serif",
    # inherit.aes = FALSE
  ) 
```

```{r}
plot1 | plot2 + plot_annotation(tag_levels = 'A')
```

